---
title: "Mixture Toxicity"
output: html_document
date: '2022-09-20'
---

# Loading libraries
```{r libraries}
library(tidyverse)
library(sjmisc)
library(janitor)
library(tibble)
library(cowplot)
library(stats) 
library(readr)
library(grid)
library(gridExtra)
library(ggplotify)
library(plotrix)
library(ggnewscale)
library(magick)
library(pdftools)
library(viridis)
library(SimplyAgree)
#library(rgl)
source("DataInput/bioscreen_functions.R")

options(repos = c(CRAN = "https://cloud.r-project.org"))
```

# Setting color palettes
```{r}
combo_alphabet_palette <- c("#9D8F8B","#90B927","#FE878B","#FFC60C","#D48D8B","#3DC19D","#8A58D5","#2BA735","#7282FF","#55D0E6","#CBDF1C","#3C99DB","#FEB380","#D37AFF","#BB9B56")
single_palette <- c("#FF9A17", "#3B83FF", "#3EFF38", "#FD73FF", "#FFD000",  "#A880FF")
single_palette_reverse <- c("#A880FF","#FFD000","#FD73FF","#3EFF38","#3B83FF","#FF9A17")
bw_palette_4conc <- c("#AAAAAA", "#808080", "#555555", "#2B2B2B")
bw_palette_5conc <- c("#AAAAAA","#888888","#666666","#434343","#212121")
```

# Data manipulation
##trial 1
```{r}
codes1 <- read.csv("DataInput/BIO1_combo_SoT_codes.csv")
codes2 <- read.csv("DataInput/BIO2_combo_SoT_codes.csv")
data1 <- read.csv("DataInput/BIO1_SoT_220922.csv")
data2 <- read.csv("DataInput/BIO2_SoT_220922.csv")

#transpose "data" so it can be bound with codes
#make first row into column names
wide_data1 <- data1 %>% 
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% 
  rownames_to_column("well")
wide_data2 <- data2 %>% 
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% 
  rownames_to_column("well")

#make data long
long_data1 <- wide_data1 %>% 
  gather("time", "OD", 2:193)
long_data2 <- wide_data2 %>% 
  gather("time", "OD", 2:193)
  
#bind data and codes
df1 <- full_join(codes1, wide_data1) %>% 
  arrange(well)
df2 <- full_join(codes2, wide_data2) %>% 
  arrange(well)

#add qualifier so well names are distinct between the two machines
df1$well<-sub("^", "BIO1", df1$well)
df2$well<-sub("^", "BIO2", df2$well)

df3_1 <- rbind(df1, df2)



code_df <- df3_1 %>% 
  select(1:5)

for(r in 1:nrow(df3_1)){
  temp = as.numeric(df3_1[r, 6:ncol(df3_1)]) # depending if the file is imported... make sure that the number is the column you want to start measuring OD
  time = seq(0.25, length(temp)/4, by = 0.25)
  growth <- spline.slope(time, temp)
  t <- spline(time, temp)
  code_df$initOD[r] <- mean(temp[3:8]) # Arbitrary choice, first between 45 min and 2.5 hours
  #code_df$OD_maxSlope[r] <- temp[which(time == t)]
  code_df$finalOD[r] <- mean(temp[(length(temp)-5):length(temp)])
  code_df$changeOD[r] <- max(temp) - min(temp)
  code_df$maxSlope[r] <- growth
  #code_df$time_maxSlope[r] <- t
  code_df$finalTime[r] <- length(temp)/4
}  


#make a new dataframe where the slopes are averaged across replicates
max_growth1_wells <- code_df %>% 
  select(!c(finalTime)) %>% 
  arrange(metal, conc, yeast, replicate)
max_growth1 <- code_df %>% 
  select(!c(well, finalTime)) %>% 
  arrange(metal, conc, yeast, replicate) %>% 
  ## There is an extra row of CdMn/conc1/trial1. Next line removes it
  filter(!(metal=="CdMn" & conc==1 & replicate==1 & maxSlope>0.24))
  
trial1_unavg <- max_growth1 %>% mutate(trial="one") %>% filter(yeast!="BLANK")
  
averages_trial1 <- max_growth1 %>% 
  filter(yeast!="BLANK") %>% 
  group_by(metal, conc) %>%
  mutate(Mean_r = mean(maxSlope),
         SE_r = std.error(maxSlope),
         Mean_OD = mean(finalOD-initOD),
         SE_OD = std.error(finalOD-initOD),
         Mean_changeOD = mean(changeOD)) %>% 
  arrange(metal, conc) %>% 
  select(metal, conc, Mean_r, SE_r, Mean_OD, SE_OD, Mean_changeOD) %>%
  distinct() %>%
  mutate(trial="one")
```

##trial 2
```{r}
codes1 <- read.csv("DataInput/BIO1_combo_SoT_codes_trial3.csv")
codes2 <- read.csv("DataInput/BIO2_combo_SoT_codes_trial3.csv")
data1 <- read.csv("DataInput/BIO1_041022.csv")
data2 <- read.csv("DataInput/BIO2_041022.csv")

#transpose "data" so it can be bound with codes
#make first row into column names
wide_data1 <- data1 %>% 
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% 
  rownames_to_column("well")
wide_data2 <- data2 %>% 
  rotate_df() %>% 
  row_to_names(row_number = 1) %>% 
  rownames_to_column("well")

#make data long
long_data1 <- wide_data1 %>% 
  gather("time", "OD", 2:193)
long_data2 <- wide_data2 %>% 
  gather("time", "OD", 2:193)
  
#bind data and codes
df1 <- full_join(codes1, wide_data1) %>% 
  arrange(well)
df2 <- full_join(codes2, wide_data2) %>% 
  arrange(well)

#add qualifier so well names are distinct between the two machines
df1$well<-sub("^", "BIO1", df1$well)
df2$well<-sub("^", "BIO2", df2$well)

df3_2 <- rbind(df1, df2)

code_df <- df3_2 %>% 
  select(1:5)

for(r in 1:nrow(df3_2)){
  temp = as.numeric(df3_2[r, 6:ncol(df3_2)]) # depending if the file is imported... make sure that the number is the column you want to start measuring OD
  time = seq(0.25, length(temp)/4, by = 0.25)
  growth <- spline.slope(time, temp)
  t <- spline(time, temp)
  code_df$initOD[r] <- mean(temp[3:8]) # Arbitrary choice, first between 45 min and 2.5 hours
  #code_df$OD_maxSlope[r] <- temp[which(time == t)]
  code_df$finalOD[r] <- mean(temp[(length(temp)-5):length(temp)])
  code_df$changeOD[r] <- max(temp) - min(temp)
  code_df$maxSlope[r] <- growth
  #code_df$time_maxSlope[r] <- t
  code_df$finalTime[r] <- length(temp)/4
}  


#make a new dataframe where the slopes are averaged across replicates
max_growth2_wells <- code_df %>% 
  select(!c(finalTime)) %>% 
  arrange(metal, conc, yeast, replicate)
max_growth2 <- code_df %>% 
  select(!c(well, finalTime)) %>% 
  arrange(metal, conc, yeast, replicate)
trial2_unavg <- max_growth2 %>% mutate(trial="two") %>% filter(yeast!="BLANK")

averages_trial2 <- max_growth2 %>% 
  filter(yeast!="BLANK") %>% 
  group_by(metal, conc) %>%
  mutate(Mean_r = mean(maxSlope),
         SE_r = std.error(maxSlope),
         Mean_OD = mean(finalOD-initOD), # mean change in OD
         SE_OD = std.error(finalOD-initOD),
         Mean_changeOD = mean(changeOD)) %>% # testing new way of mean change in OD
  arrange(metal, conc) %>% 
  select(metal, conc, Mean_r, SE_r, Mean_OD, SE_OD, Mean_changeOD) %>%
  distinct() %>% 
  mutate(trial="two")
```

##joining trials 1 and 2
```{r}
vgraph_mM <- read.csv("DataInput/vgraph_concs.csv") %>% 
  pivot_longer(cols=c(trial1_mM, trial2_mM), names_to = "trial", values_to = "mM")
vgraph_mM$trial <- sub("trial1_mM", "one", vgraph_mM$trial)
vgraph_mM$trial <- sub("trial2_mM", "two", vgraph_mM$trial)

combodata_unavg <- rbind(trial1_unavg, trial2_unavg) %>% 
  left_join(vgraph_mM, by = join_by(metal, conc, trial)) %>% 
  relocate(mM, .after=trial) %>% 
  arrange(metal, trial, conc, replicate)

combodata_avg <- rbind(averages_trial1, averages_trial2) 
combodata_avg$conc <- as.character(combodata_avg$conc)
write_csv(combodata_avg, "DataOutput/vgraph_growthrates_avg.csv")
```
## Examining blanks
```{r}
blanks1_unavg <- max_growth1 %>% 
  arrange(metal, conc, yeast, replicate) %>% 
  filter(yeast=="BLANK") %>% 
  filter(maxSlope<0.1)
blanks1 <- blanks1_unavg %>% 
  group_by(metal) %>% 
  summarise(avg_blank = mean(maxSlope),
            SE = std.error(maxSlope))

blanks2_unavg <- max_growth2 %>% 
  arrange(metal, conc, yeast, replicate) %>% 
  filter(yeast=="BLANK") %>% 
filter(maxSlope<0.1)
blanks2 <- blanks2_unavg %>% 
  group_by(metal) %>% 
  summarise(avg_blank = mean(maxSlope),
            SE = std.error(maxSlope))

blanks_unavg <- rbind(blanks1_unavg,blanks2_unavg) %>% select(c(metal, yeast, maxSlope))
blanks_unavg %>% write_csv("DataOutput/vgraph_blanks.csv")

blanks1 %>% ggplot(aes(x=metal, y=avg_blank)) +
  geom_point() +
  geom_errorbar(aes(ymin=avg_blank-SE, ymax=avg_blank+SE), 
                width=0.1, position=position_dodge(width=0.7)) +
  lims(y=c(0,0.3)) +
  theme_bw()

blanks2 %>% ggplot(aes(x=metal, y=avg_blank)) +
  geom_point() +
  geom_errorbar(aes(ymin=avg_blank-SE, ymax=avg_blank+SE), 
                width=0.1, position=position_dodge(width=0.7)) +
  lims(y=c(0,0.3)) +
  theme_bw()

blanks_unavg %>% 
  ggplot(aes(x=metal, y=maxSlope, color=metal)) +
  geom_point()+
  lims(y=c(0,0.3)) +
  theme_bw() +
  facet_wrap(~metal)
```
# Figure 1
## fig1A pieces - max growth rates
```{r}
#FOR COMPOSITE V-GRAPH

#color gradients determined with hihayk.github.io/scale

# 0 angle, 50% darkness, 50% dark sat, 60% lightness, 75% light sat

a <- combodata_avg %>% 
  filter(metal=="Cd" | metal=="CdCo" | metal=="Co") %>% 
  ggplot(aes(x=metal,y=Mean_r,color=as.character(conc), shape=as.character(trial))) +
  #geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=0.2) +
  geom_point(size=2) +
  geom_hline(yintercept = 0.3273644, alpha=0.5) +
  geom_hline(yintercept = 0.0238344, alpha=0.5) +
  scale_color_manual(values=c("#DBD1CE", "#BDAFAB", "#9D8F8B", "#776A67", "#514643")) +
  ylim(0.0,0.341) +
  theme_light() +
  theme(legend.position = "none",
        panel.border=element_rect(color="white"),
        panel.grid.minor = element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=7),
        plot.margin=margin(0,0,5,0))

# 0 angle, 50% darkness,50% dark sat, 50% lightness,75% light sat
b <- combodata_avg %>% 
  filter(metal=="Cd" | metal=="CdCu" | metal=="Cu") %>% 
  ggplot(aes(x=metal,y=Mean_r,color=as.character(conc), shape=as.character(trial))) +
  #geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=0.2) +
  geom_hline(yintercept = 0.3273644, alpha=0.5) +
  geom_hline(yintercept = 0.0238344, alpha=0.5) +
  geom_point(size=2) +
  scale_color_manual(values=c("#D4F780","#B5DF49","#90B927", "#729810","#506F01")) +
  ylim(0.0,0.34) +
  theme_light() +
  theme(legend.position = "none",
        panel.border=element_rect(color="white"),
        panel.grid.minor = element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=7),
        plot.margin=margin(0,0,5,0))

# 0 angle, 50% darkness, 50% dark sat, 60% lightness, 75% light sat
c <- combodata_avg %>% 
  filter(metal=="Cd" | metal=="CdMn" | metal=="Mn") %>% 
  ggplot(aes(x=metal,y=Mean_r,color=as.character(conc), shape=as.character(trial))) +
  #geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=0.2) +
  geom_hline(yintercept = 0.3273644, alpha=0.5) +
  geom_hline(yintercept = 0.0238344, alpha=0.5) +
  geom_point(size=2) +
  scale_color_manual(values=c("#FFBDC0","#FF9B9F","#FE878B","#BF5A5E","#803538")) +
  ylim(0.0,0.34) +
  theme_light() +
  theme(legend.position = "none",
        panel.border=element_rect(color="white"),
        panel.grid.minor = element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=7),
        plot.margin=margin(0,0,5,0))

# 0 angle, 24% darkness, 50 dark sat, 25% lightness, 51% light sat
d <- combodata_avg %>% 
  filter(metal=="Cd" | metal=="CdNi" | metal=="Ni") %>% 
  ggplot(aes(x=metal,y=Mean_r,color=as.character(conc), shape=as.character(trial))) +
  #geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=0.2) +
  geom_hline(yintercept = 0.3273644, alpha=0.5) +
  geom_hline(yintercept = 0.0238344, alpha=0.5) +
  geom_point(size=2) +
  scale_color_manual(values=c("#FFED40","#FFDC20","#FFC60C","#C6A600","#8C7F00")) +
  ylim(0.0,0.34) +
  theme_light() +
  theme(legend.position = "none",
        panel.border=element_rect(color="white"),
        panel.grid.minor = element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=7),
        plot.margin=margin(0,0,5,0))

# 0 angle, 50% darkness, 50% dark sat, 60% lightness, 75% light sat
e <- combodata_avg %>% 
  filter(metal=="Cd" | metal=="CdZn" | metal=="Zn") %>% 
  ggplot(aes(x=metal,y=Mean_r,color=as.character(conc), shape=as.character(trial))) +
  #geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=0.2) +
  geom_hline(yintercept = 0.3273644, alpha=0.5) +
  geom_hline(yintercept = 0.0238344, alpha=0.5) +
  geom_point(size=2) +
  scale_color_manual(values=c("#F9C7C6","#EBA6A4","#D48D8B","#A66361","#733E3C")) +
  ylim(0.0,0.34) +
  theme_light() +
  theme(legend.position = "none",
        panel.border=element_rect(color="white"),
        panel.grid.minor = element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=7),
        plot.margin=margin(0,0,5,0))

# 0 angle, 50% darkness, 50% dark sat, 65% lightness, 25% light sat
f <- combodata_avg %>% 
  filter(metal=="Co" | metal=="CoCu" | metal=="Cu") %>% 
  ggplot(aes(x=metal,y=Mean_r,color=as.character(conc), shape=as.character(trial))) +
  #geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=0.2) +
  geom_hline(yintercept = 0.3273644, alpha=0.5) +
  geom_hline(yintercept = 0.0238344, alpha=0.5) +
  geom_point(size=2) +
  scale_color_manual(values=c("#96E8D2","#67D7B8","#3DC19D","#219D7B","#0E7156")) +
  ylim(0.0,0.34) +
  theme_light() +
  theme(legend.position = "none",
        panel.border=element_rect(color="white"),
        panel.grid.minor = element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=7),
        plot.margin=margin(0,0,5,0))

# 0 angle, 50% darkness, 50% dark sat, 65% lightness, 50% light sat
g <- combodata_avg %>% 
  filter(metal=="Co" | metal=="CoMn" | metal=="Mn") %>% 
  ggplot(aes(x=metal,y=Mean_r,color=as.character(conc), shape=as.character(trial))) +
  #geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=0.2) +
  geom_hline(yintercept = 0.3273644, alpha=0.5) +
  geom_hline(yintercept = 0.0238344, alpha=0.5) +
  geom_point(size=2) +
  scale_color_manual(values=c("#D3B7FD","#AE82EF","#8A58D5","#6536AC","#421C7A")) +
  ylim(0.0,0.34) +
  theme_light() +
  theme(legend.position = "none",
        panel.border=element_rect(color="white"),
        panel.grid.minor = element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=7),
        plot.margin=margin(0,0,5,0))

# 0 angle, 50% darkness, 50% dark sat, 65% lightness, 75% light sat
h <- combodata_avg %>% 
  filter(metal=="Co" | metal=="CoNi" | metal=="Ni") %>% 
  ggplot(aes(x=metal,y=Mean_r,color=as.character(conc), shape=as.character(trial))) +
  #geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=0.2) +
  geom_hline(yintercept = 0.3273644, alpha=0.5) +
  geom_hline(yintercept = 0.0238344, alpha=0.5) +
  geom_point(size=2) +
  scale_color_manual(values=c("#A6F1AB","#60D36A","#2BA735","#15891E","#06630E")) +
  ylim(0.0,0.34) +
  theme_light() +
  theme(legend.position = "none",
        panel.border=element_rect(color="white"),
        panel.grid.minor = element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=7),
        plot.margin=margin(0,0,5,0))

# 0 angle, 50% darkness, 50% dark sat, 65% lightness, 60% light sat
i <- combodata_avg %>% 
  filter(metal=="Co" | metal=="CoZn" | metal=="Zn") %>% 
  ggplot(aes(x=metal,y=Mean_r,color=as.character(conc), shape=as.character(trial))) +
  #geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=0.2) +
  geom_hline(yintercept = 0.3273644, alpha=0.5) +
  geom_hline(yintercept = 0.0238344, alpha=0.5) +
  geom_point(size=2) +
  scale_color_manual(values=c("#BFC8FF","#92A0FF","#7282FF","#4857BF","#273380")) +
  ylim(0.0,0.34) +
  theme_light() +
  theme(legend.position = "none",
        panel.border=element_rect(color="white"),
        panel.grid.minor = element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=7),
        plot.margin=margin(0,0,5,0))

# 0 angle, 50% darkness, 50% dark sat,
j <- combodata_avg %>% 
  filter(metal=="Cu" | metal=="CuMn" | metal=="Mn") %>% 
  ggplot(aes(x=metal,y=Mean_r,color=as.character(conc), shape=as.character(trial))) +
  #geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=0.2) +
  geom_hline(yintercept = 0.3273644, alpha=0.5) +
  geom_hline(yintercept = 0.0238344, alpha=0.5) +
  geom_point(size=2) +
  scale_color_manual(values=c("#A1EEFC","#79E1F3","#55D0E6","#32A6BA","#187580")) +
  ylim(0.0,0.34) +
  theme_light() +
  theme(legend.position = "none",
        panel.border=element_rect(color="white"),
        panel.grid.minor = element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=7),
        plot.margin=margin(0,0,5,0))

# 0 angle, 50% darkness, 50% dark sat, 0% lightness, 30% light sat
k <- combodata_avg %>% 
  filter(metal=="Cu" | metal=="CuNi" | metal=="Ni") %>% 
  ggplot(aes(x=metal,y=Mean_r,color=as.character(conc), shape=as.character(trial))) +
  #geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=0.2) +
  geom_hline(yintercept = 0.3273644, alpha=0.5) +
  geom_hline(yintercept = 0.0238344, alpha=0.5) +
  geom_point(size=2) +
  scale_color_manual(values=c("#E7F473","#DAEB46","#CBDF1C","#A7BA03","#798000")) +
  ylim(0.0,0.34) +
  theme_light() +
  theme(legend.position = "none",
        panel.border=element_rect(color="white"),
        panel.grid.minor = element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=7),
        plot.margin=margin(0,0,5,0))

# 0 angle, 50% darkness, 50% dark sat, 60% lightness, 50% light sat
l <- combodata_avg %>% 
  filter(metal=="Cu" | metal=="CuZn" | metal=="Zn") %>% 
  ggplot(aes(x=metal,y=Mean_r,color=as.character(conc), shape=as.character(trial))) +
  #geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=0.2) +
  geom_hline(yintercept = 0.3273644, alpha=0.5) +
  geom_hline(yintercept = 0.0238344, alpha=0.5) +
  geom_point(size=2) +
  scale_color_manual(values=c("#A1D9FF","#69BAF4","#3C99DB","#1E75B3","#0A5080")) +
  ylim(0.0,0.34) +
  theme_light() +
  theme(legend.position = "none",
        panel.border=element_rect(color="white"),
        panel.grid.minor = element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=7),
        plot.margin=margin(0,0,5,0))

# 0 angle, 30% darkness, 50% dark sat, 50% lightness, 50% light sat
m <- combodata_avg %>% 
  filter(metal=="Mn" | metal=="MnNi" | metal=="Ni") %>% 
  ggplot(aes(x=metal,y=Mean_r,color=as.character(conc), shape=as.character(trial))) +
  #geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=0.2) +
  geom_hline(yintercept = 0.3273644, alpha=0.5) +
  geom_hline(yintercept = 0.0238344, alpha=0.5) +
  geom_point(size=2) +
  scale_color_manual(values=c("#FFD6B0","#FFC494","#FEB380","#D9965F","#B37944")) +
  ylim(0.0,0.34) +
  theme_light() +
  theme(legend.position = "none",
        panel.border=element_rect(color="white"),
        panel.grid.minor = element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=7),
        plot.margin=margin(0,0,5,0))

# 0 angle, 50% darkness, 50% dark sat, 60% lightness, 25% light sat
n <- combodata_avg %>% 
  filter(metal=="Mn" | metal=="MnZn" | metal=="Zn") %>% 
  ggplot(aes(x=metal,y=Mean_r,color=as.character(conc), shape=as.character(trial))) +
  #geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=0.2) +
  geom_hline(yintercept = 0.3273644, alpha=0.5) +
  geom_hline(yintercept = 0.0238344, alpha=0.5) +
  geom_point(size=2) +
  scale_color_manual(values=c("#F0C3FF","#E29CFF","#D37AFF","#A34FBF","#6F2C80")) +
  ylim(0.0,0.34) +
  theme_light() +
  theme(legend.position = "none",
        panel.border=element_rect(color="white"),
        panel.grid.minor = element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=7),
        plot.margin=margin(0,0,5,0))

# 0 angle, 50% darkness, 50% dark sat, 65% lightness, 75% light sat
o <- combodata_avg %>% 
  filter(metal=="Ni" | metal=="NiZn" | metal=="Zn") %>% 
  ggplot(aes(x=metal,y=Mean_r,color=as.character(conc), shape=as.character(trial))) +
  #geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=0.2) +
  geom_hline(yintercept = 0.3273644, alpha=0.5) +
  geom_hline(yintercept = 0.0238344, alpha=0.5) +
  geom_point(size=2) +
  scale_color_manual(values=c("#F5E1B7","#DEC080","#BB9B56","#967837","#6A521E")) +
  ylim(0.0,0.34) +
  theme_light() +
  theme(legend.position = "none",
        panel.border=element_rect(color="white"),
        panel.grid.minor = element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.text.x=element_text(size=7),
        plot.margin=margin(0,0,5,0))

fig1A <- plot_grid(e,d,c,b,a,i,h,g,f,NULL,l,k,j,NULL,NULL,n,m,NULL,NULL,NULL,o,NULL,NULL,NULL,NULL, ncol=5, rel_widths = c(1,1,1,1,1), scale = 0.98)
fig1A_component <- ggdraw() +
  draw_plot(fig1A) +
  draw_line(x=c(0.001,0.001,0.999,0.999,0.001),y=c(0.001,0.999,0.999,0.8,0.8), size=0.2) +
  draw_line(x=c(0.001,0.8,0.8),y=c(0.6,0.6,0.999), size=0.2) +
  draw_line(x=c(0.001,0.6,0.6),y=c(0.4,0.4,0.999), size=0.2) +
  draw_line(x=c(0.001,0.4,0.4),y=c(0.2,0.2,0.999), size=0.2) +
  draw_line(x=c(0.001,0.2,0.2),y=c(0.001,0.001,0.999), size=0.2) +
  draw_label("Zn", x=0.1, y=1.03, size=12) +
  draw_label("Ni", x=0.3, y=1.03, size=12) +
  draw_label("Mn", x=0.5, y=1.03, size=12) +
  draw_label("Cu", x=0.7, y=1.03, size=12) +
  draw_label("Co", x=0.9, y=1.03, size=12) +
  draw_label("Cd", x=-0.03, y=0.9, size=12) +
  draw_label("Co", x=-0.03, y=0.7, size=12) +
  draw_label("Cu", x=-0.03, y=0.5, size=12) +
  draw_label("Mn", x=-0.03, y=0.3, size=12)+
  draw_label("Ni", x=-0.03, y=0.1, size=12)
```
##calculating delta
###delta_r
```{r}
CdCo <- combodata_avg %>% 
  filter(metal=="Cd" | metal=="Co" | metal=="CdCo") %>% 
  mutate(combo="CdCo") %>% 
  mutate(component=case_when(metal=="Cd" ~ "met1_r",
                   metal=="Co" ~ "met2_r",
                   metal=="CdCo" ~ "combo_r")) %>% 
  select(c(trial, combo, conc, component, Mean_r)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_r) %>% 
  mutate(delta_r=1-(combo_r/((met1_r+met2_r)/2)))

CdCu <- combodata_avg %>% 
  filter(metal=="Cd" | metal=="Cu" | metal=="CdCu") %>% 
  mutate(combo="CdCu") %>% 
  mutate(component=case_when(metal=="Cd" ~ "met1_r",
                   metal=="Cu" ~ "met2_r",
                   metal=="CdCu" ~ "combo_r")) %>% 
  select(c(trial, combo, conc, component, Mean_r)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_r) %>% 
  mutate(delta_r=1-(combo_r/((met1_r+met2_r)/2)))

CdMn <- combodata_avg %>% 
  filter(metal=="Cd" | metal=="Mn" | metal=="CdMn") %>% 
  mutate(combo="CdMn") %>% 
  mutate(component=case_when(metal=="Cd" ~ "met1_r",
                   metal=="Mn" ~ "met2_r",
                   metal=="CdMn" ~ "combo_r")) %>% 
  select(c(trial, combo, conc, component, Mean_r)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_r) %>% 
  mutate(delta_r=1-(combo_r/((met1_r+met2_r)/2)))

CdNi <- combodata_avg %>% 
  filter(metal=="Cd" | metal=="Ni" | metal=="CdNi") %>% 
  mutate(combo="CdNi") %>% 
  mutate(component=case_when(metal=="Cd" ~ "met1_r",
                   metal=="Ni" ~ "met2_r",
                   metal=="CdNi" ~ "combo_r")) %>% 
  select(c(trial, combo, conc, component, Mean_r)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_r) %>% 
  mutate(delta_r=1-(combo_r/((met1_r+met2_r)/2)))

CdZn <- combodata_avg %>% 
  filter(metal=="Cd" | metal=="Zn" | metal=="CdZn") %>% 
  mutate(combo="CdZn") %>% 
  mutate(component=case_when(metal=="Cd" ~ "met1_r",
                   metal=="Zn" ~ "met2_r",
                   metal=="CdZn" ~ "combo_r")) %>% 
  select(c(trial, combo, conc, component, Mean_r)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_r) %>% 
  mutate(delta_r=1-(combo_r/((met1_r+met2_r)/2)))

CoCu <- combodata_avg %>% 
  filter(metal=="Co" | metal=="Cu" | metal=="CoCu") %>% 
  mutate(combo="CoCu") %>% 
  mutate(component=case_when(metal=="Co" ~ "met1_r",
                   metal=="Cu" ~ "met2_r",
                   metal=="CoCu" ~ "combo_r")) %>% 
  select(c(trial, combo, conc, component, Mean_r)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_r) %>% 
  mutate(delta_r=1-(combo_r/((met1_r+met2_r)/2)))

CoMn <- combodata_avg %>% 
  filter(metal=="Co" | metal=="Mn" | metal=="CoMn") %>% 
  mutate(combo="CoMn") %>% 
  mutate(component=case_when(metal=="Co" ~ "met1_r",
                   metal=="Mn" ~ "met2_r",
                   metal=="CoMn" ~ "combo_r")) %>% 
  select(c(trial, combo, conc, component, Mean_r)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_r) %>% 
  mutate(delta_r=1-(combo_r/((met1_r+met2_r)/2)))

CoNi <- combodata_avg %>% 
  filter(metal=="Co" | metal=="Ni" | metal=="CoNi") %>% 
  mutate(combo="CoNi") %>% 
  mutate(component=case_when(metal=="Co" ~ "met1_r",
                   metal=="Ni" ~ "met2_r",
                   metal=="CoNi" ~ "combo_r")) %>% 
  select(c(trial, combo, conc, component, Mean_r)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_r) %>% 
  mutate(delta_r=1-(combo_r/((met1_r+met2_r)/2)))

CoZn <- combodata_avg %>% 
  filter(metal=="Co" | metal=="Zn" | metal=="CoZn") %>% 
  mutate(combo="CoZn") %>% 
  mutate(component=case_when(metal=="Co" ~ "met1_r",
                   metal=="Zn" ~ "met2_r",
                   metal=="CoZn" ~ "combo_r")) %>% 
  select(c(trial, combo, conc, component, Mean_r)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_r) %>% 
  mutate(delta_r=1-(combo_r/((met1_r+met2_r)/2)))

CuMn <- combodata_avg %>% 
  filter(metal=="Cu" | metal=="Mn" | metal=="CuMn") %>% 
  mutate(combo="CuMn") %>% 
  mutate(component=case_when(metal=="Cu" ~ "met1_r",
                   metal=="Mn" ~ "met2_r",
                   metal=="CuMn" ~ "combo_r")) %>% 
  select(c(trial, combo, conc, component, Mean_r)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_r) %>% 
  mutate(delta_r=1-(combo_r/((met1_r+met2_r)/2)))

CuNi <- combodata_avg %>% 
  filter(metal=="Cu" | metal=="Ni" | metal=="CuNi") %>% 
  mutate(combo="CuNi") %>% 
  mutate(component=case_when(metal=="Cu" ~ "met1_r",
                   metal=="Ni" ~ "met2_r",
                   metal=="CuNi" ~ "combo_r")) %>% 
  select(c(trial, combo, conc, component, Mean_r)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_r) %>% 
  mutate(delta_r=1-(combo_r/((met1_r+met2_r)/2)))

CuZn <- combodata_avg %>% 
  filter(metal=="Cu" | metal=="Zn" | metal=="CuZn") %>% 
  mutate(combo="CuZn") %>% 
  mutate(component=case_when(metal=="Cu" ~ "met1_r",
                   metal=="Zn" ~ "met2_r",
                   metal=="CuZn" ~ "combo_r")) %>% 
  select(c(trial, combo, conc, component, Mean_r)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_r) %>% 
  mutate(delta_r=1-(combo_r/((met1_r+met2_r)/2)))

MnNi <- combodata_avg %>% 
  filter(metal=="Mn" | metal=="Ni" | metal=="MnNi") %>% 
  mutate(combo="MnNi") %>% 
  mutate(component=case_when(metal=="Mn" ~ "met1_r",
                   metal=="Ni" ~ "met2_r",
                   metal=="MnNi" ~ "combo_r")) %>% 
  select(c(trial, combo, conc, component, Mean_r)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_r) %>% 
  mutate(delta_r=1-(combo_r/((met1_r+met2_r)/2)))

MnZn <- combodata_avg %>% 
  filter(metal=="Mn" | metal=="Zn" | metal=="MnZn") %>% 
  mutate(combo="MnZn") %>% 
  mutate(component=case_when(metal=="Mn" ~ "met1_r",
                   metal=="Zn" ~ "met2_r",
                   metal=="MnZn" ~ "combo_r")) %>% 
  select(c(trial, combo, conc, component, Mean_r)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_r) %>% 
  mutate(delta_r=1-(combo_r/((met1_r+met2_r)/2)))

NiZn <- combodata_avg %>% 
  filter(metal=="Ni" | metal=="Zn" | metal=="NiZn") %>% 
  mutate(combo="NiZn") %>% 
  mutate(component=case_when(metal=="Ni" ~ "met1_r",
                   metal=="Zn" ~ "met2_r",
                   metal=="NiZn" ~ "combo_r")) %>% 
  select(c(trial, combo, conc, component, Mean_r)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_r) %>% 
  mutate(delta_r=1-(combo_r/((met1_r+met2_r)/2)))

delta_r_df <- rbind(CdCo, CdCu, CdMn, CdNi, CdZn, CoCu, CoMn, CoNi, CoZn, CuMn, CuNi, CuZn, MnNi, MnZn, NiZn)
delta_r_df %>% write.csv("DataOutput/delta_r_df.csv")
```
###delta_OD
```{r}
CdCo <- combodata_avg %>% 
  filter(metal=="Cd" | metal=="Co" | metal=="CdCo") %>% 
  mutate(combo="CdCo") %>% 
  mutate(component=case_when(metal=="Cd" ~ "met1_changeOD",
                   metal=="Co" ~ "met2_changeOD",
                   metal=="CdCo" ~ "combo_changeOD")) %>% 
  select(c(trial, combo, conc, component, Mean_changeOD)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_changeOD) %>% 
  mutate(delta_changeOD=1-(combo_changeOD/((met1_changeOD+met2_changeOD)/2)))

CdCu <- combodata_avg %>% 
  filter(metal=="Cd" | metal=="Cu" | metal=="CdCu") %>% 
  mutate(combo="CdCu") %>% 
  mutate(component=case_when(metal=="Cd" ~ "met1_changeOD",
                   metal=="Cu" ~ "met2_changeOD",
                   metal=="CdCu" ~ "combo_changeOD")) %>% 
  select(c(trial, combo, conc, component, Mean_changeOD)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_changeOD) %>% 
  mutate(delta_changeOD=1-(combo_changeOD/((met1_changeOD+met2_changeOD)/2)))

CdMn <- combodata_avg %>% 
  filter(metal=="Cd" | metal=="Mn" | metal=="CdMn") %>% 
  mutate(combo="CdMn") %>% 
  mutate(component=case_when(metal=="Cd" ~ "met1_changeOD",
                   metal=="Mn" ~ "met2_changeOD",
                   metal=="CdMn" ~ "combo_changeOD")) %>% 
  select(c(trial, combo, conc, component, Mean_changeOD)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_changeOD) %>% 
  mutate(delta_changeOD=1-(combo_changeOD/((met1_changeOD+met2_changeOD)/2)))

CdNi <- combodata_avg %>% 
  filter(metal=="Cd" | metal=="Ni" | metal=="CdNi") %>% 
  mutate(combo="CdNi") %>% 
  mutate(component=case_when(metal=="Cd" ~ "met1_changeOD",
                   metal=="Ni" ~ "met2_changeOD",
                   metal=="CdNi" ~ "combo_changeOD")) %>% 
  select(c(trial, combo, conc, component, Mean_changeOD)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_changeOD) %>% 
  mutate(delta_changeOD=1-(combo_changeOD/((met1_changeOD+met2_changeOD)/2)))

CdZn <- combodata_avg %>% 
  filter(metal=="Cd" | metal=="Zn" | metal=="CdZn") %>% 
  mutate(combo="CdZn") %>% 
  mutate(component=case_when(metal=="Cd" ~ "met1_changeOD",
                   metal=="Zn" ~ "met2_changeOD",
                   metal=="CdZn" ~ "combo_changeOD")) %>% 
  select(c(trial, combo, conc, component, Mean_changeOD)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_changeOD) %>% 
  mutate(delta_changeOD=1-(combo_changeOD/((met1_changeOD+met2_changeOD)/2)))

CoCu <- combodata_avg %>% 
  filter(metal=="Co" | metal=="Cu" | metal=="CoCu") %>% 
  mutate(combo="CoCu") %>% 
  mutate(component=case_when(metal=="Co" ~ "met1_changeOD",
                   metal=="Cu" ~ "met2_changeOD",
                   metal=="CoCu" ~ "combo_changeOD")) %>% 
  select(c(trial, combo, conc, component, Mean_changeOD)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_changeOD) %>% 
  mutate(delta_changeOD=1-(combo_changeOD/((met1_changeOD+met2_changeOD)/2)))

CoMn <- combodata_avg %>% 
  filter(metal=="Co" | metal=="Mn" | metal=="CoMn") %>% 
  mutate(combo="CoMn") %>% 
  mutate(component=case_when(metal=="Co" ~ "met1_changeOD",
                   metal=="Mn" ~ "met2_changeOD",
                   metal=="CoMn" ~ "combo_changeOD")) %>% 
  select(c(trial, combo, conc, component, Mean_changeOD)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_changeOD) %>% 
  mutate(delta_changeOD=1-(combo_changeOD/((met1_changeOD+met2_changeOD)/2)))

CoNi <- combodata_avg %>% 
  filter(metal=="Co" | metal=="Ni" | metal=="CoNi") %>% 
  mutate(combo="CoNi") %>% 
  mutate(component=case_when(metal=="Co" ~ "met1_changeOD",
                   metal=="Ni" ~ "met2_changeOD",
                   metal=="CoNi" ~ "combo_changeOD")) %>% 
  select(c(trial, combo, conc, component, Mean_changeOD)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_changeOD) %>% 
  mutate(delta_changeOD=1-(combo_changeOD/((met1_changeOD+met2_changeOD)/2)))

CoZn <- combodata_avg %>% 
  filter(metal=="Co" | metal=="Zn" | metal=="CoZn") %>% 
  mutate(combo="CoZn") %>% 
  mutate(component=case_when(metal=="Co" ~ "met1_changeOD",
                   metal=="Zn" ~ "met2_changeOD",
                   metal=="CoZn" ~ "combo_changeOD")) %>% 
  select(c(trial, combo, conc, component, Mean_changeOD)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_changeOD) %>% 
  mutate(delta_changeOD=1-(combo_changeOD/((met1_changeOD+met2_changeOD)/2)))

CuMn <- combodata_avg %>% 
  filter(metal=="Cu" | metal=="Mn" | metal=="CuMn") %>% 
  mutate(combo="CuMn") %>% 
  mutate(component=case_when(metal=="Cu" ~ "met1_changeOD",
                   metal=="Mn" ~ "met2_changeOD",
                   metal=="CuMn" ~ "combo_changeOD")) %>% 
  select(c(trial, combo, conc, component, Mean_changeOD)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_changeOD) %>% 
  mutate(delta_changeOD=1-(combo_changeOD/((met1_changeOD+met2_changeOD)/2)))

CuNi <- combodata_avg %>% 
  filter(metal=="Cu" | metal=="Ni" | metal=="CuNi") %>% 
  mutate(combo="CuNi") %>% 
  mutate(component=case_when(metal=="Cu" ~ "met1_changeOD",
                   metal=="Ni" ~ "met2_changeOD",
                   metal=="CuNi" ~ "combo_changeOD")) %>% 
  select(c(trial, combo, conc, component, Mean_changeOD)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_changeOD) %>% 
  mutate(delta_changeOD=1-(combo_changeOD/((met1_changeOD+met2_changeOD)/2)))

CuZn <- combodata_avg %>% 
  filter(metal=="Cu" | metal=="Zn" | metal=="CuZn") %>% 
  mutate(combo="CuZn") %>% 
  mutate(component=case_when(metal=="Cu" ~ "met1_changeOD",
                   metal=="Zn" ~ "met2_changeOD",
                   metal=="CuZn" ~ "combo_changeOD")) %>% 
  select(c(trial, combo, conc, component, Mean_changeOD)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_changeOD) %>% 
  mutate(delta_changeOD=1-(combo_changeOD/((met1_changeOD+met2_changeOD)/2)))

MnNi <- combodata_avg %>% 
  filter(metal=="Mn" | metal=="Ni" | metal=="MnNi") %>% 
  mutate(combo="MnNi") %>% 
  mutate(component=case_when(metal=="Mn" ~ "met1_changeOD",
                   metal=="Ni" ~ "met2_changeOD",
                   metal=="MnNi" ~ "combo_changeOD")) %>% 
  select(c(trial, combo, conc, component, Mean_changeOD)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_changeOD) %>% 
  mutate(delta_changeOD=1-(combo_changeOD/((met1_changeOD+met2_changeOD)/2)))

MnZn <- combodata_avg %>% 
  filter(metal=="Mn" | metal=="Zn" | metal=="MnZn") %>% 
  mutate(combo="MnZn") %>% 
  mutate(component=case_when(metal=="Mn" ~ "met1_changeOD",
                   metal=="Zn" ~ "met2_changeOD",
                   metal=="MnZn" ~ "combo_changeOD")) %>% 
  select(c(trial, combo, conc, component, Mean_changeOD)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_changeOD) %>% 
  mutate(delta_changeOD=1-(combo_changeOD/((met1_changeOD+met2_changeOD)/2)))

NiZn <- combodata_avg %>% 
  filter(metal=="Ni" | metal=="Zn" | metal=="NiZn") %>% 
  mutate(combo="NiZn") %>% 
  mutate(component=case_when(metal=="Ni" ~ "met1_changeOD",
                   metal=="Zn" ~ "met2_changeOD",
                   metal=="NiZn" ~ "combo_changeOD")) %>% 
  select(c(trial, combo, conc, component, Mean_changeOD)) %>% 
  pivot_wider(id_cols=c(trial, combo, conc), names_from = component, values_from = Mean_changeOD) %>% 
  mutate(delta_changeOD=1-(combo_changeOD/((met1_changeOD+met2_changeOD)/2)))

delta_OD_df <- rbind(CdCo, CdCu, CdMn, CdNi, CdZn, CoCu, CoMn, CoNi, CoZn, CuMn, CuNi, CuZn, MnNi, MnZn, NiZn)
```

###normality of delta
```{r}
#all deltas calculated from each conc
delta_df_4conc <- delta_r_df %>% filter(!(conc==5))
norm_unavg_deltas <- delta_df_4conc$delta_r

hist(norm_unavg_deltas, breaks=10,
     main=NULL, xlab="\u03b4")

qqnorm(norm_unavg_deltas, pch = 1, frame = FALSE,
       main=NULL)
qqline(norm_unavg_deltas, col = "steelblue", lwd = 2)

shapiro.test(norm_unavg_deltas)

#deltas averaged across conc in each combo
delta_r_avg <- delta_df_4conc %>% 
  group_by(combo) %>% 
  summarise(avg_delta=mean(delta_r))
norm_avg_deltas <- delta_r_avg$avg_delta

hist(norm_avg_deltas, breaks=10,
     main=NULL, xlab="Average \u03b4 (by combo)")

qqnorm(norm_avg_deltas, pch = 1, frame = FALSE,
       main=NULL)
qqline(norm_avg_deltas, col = "steelblue", lwd = 2)

shapiro.test(norm_avg_deltas)
```
## fig1C - observed deltas
```{r}
deltas_avg <- delta_r_df %>% 
  filter(conc!=5) %>%
  group_by(combo) %>%  
  summarise(avg_delta=mean(delta_r), se_delta=std.error(delta_r))
deltas_unavg_4conc <- delta_r_df %>% 
  filter(conc!=5) 
deltas_conc5 <- delta_r_df %>% 
  filter(conc==5)

fig1C <- deltas_avg %>% 
  mutate(combo = fct_reorder(combo, -avg_delta)) %>%
  ggplot(aes(x=combo, y=avg_delta, fill=combo)) +
  geom_hline(yintercept = 0, color="black", linewidth=0.5, alpha=0.5) +
  geom_point(aes(color=combo), position=position_dodge(width=0.7), size=6) +
  scale_color_manual(values = c("#3DC19D","#CBDF1C","#3C99DB","#BB9B56","#7282FF","#90B927", "#D48D8B","#2BA735","#9D8F8B","#FFC60C","#FE878B","#FEB380","#8A58D5","#D37AFF","#55D0E6")) +
  geom_errorbar(aes(ymin=avg_delta-se_delta, ymax=avg_delta+se_delta), width=0.75, position=position_dodge(width=0.7)) +
  new_scale_color() +
  geom_jitter(data=deltas_unavg_4conc, aes(y=delta_r, color=as.character(conc), shape=as.character(trial)), position=position_jitter(0), size=1.5) +
  scale_color_manual(values=bw_palette_4conc) +
  geom_point(data=deltas_conc5, aes(y=delta_r), shape=21, color="#242424", fill="transparent", size=1) +
  labs(x="Metal combination", y="\u03b4") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text.x = element_text(angle=45, vjust=0.7),
        #axis.title = element_text(face="bold"),
        panel.grid.major = element_line(size=0.25),
        panel.grid.minor = element_blank())
```

## Fig1_cowplot
```{r}
fig1B <- image_read_pdf("DataInput/Fig1B.pdf", density = 200)
triangle <- image_read("DataInput/triangle-png-28.png", density = 200)

ggdraw() +
  draw_grob(rectGrob(gp=gpar(col="white"))) +
  draw_plot(fig1A_component, width = 0.709, height = 0.922, x = 0.04, y = 0.015) +
  draw_plot(fig1C, width = 0.522, height = 0.55, x = 0.475, y = 0.002) +
  draw_image(fig1B, scale = 0.394, x = 0.374, y = 0.248) +
  draw_plot_label("A", x=0, y=0.991) +
  draw_plot_label("B", x=0.751, y=0.991) +
  draw_plot_label("C", x=0.47, y=0.555) +
  draw_label("Concentration level", x=0.395,y=0.3445,size=9) +
  draw_grob(circleGrob(x=0.345,y=0.315,r=0.007,gp=gpar(fill="#AAAAAA",col="transparent"))) +
  draw_grob(circleGrob(x=0.345,y=0.2855,r=0.007,gp=gpar(fill="#888888",col="transparent"))) +
  draw_grob(circleGrob(x=0.345,y=0.256,r=0.007,gp=gpar(fill="#666666",col="transparent"))) +
  draw_grob(circleGrob(x=0.345,y=0.2265,r=0.007,gp=gpar(fill="#434343",col="transparent"))) +
  draw_grob(circleGrob(x=0.345,y=0.197,r=0.007,gp=gpar(fill="#212121",col="transparent"))) +
  draw_label("1", x=0.365, y=0.315, size=9) + draw_label("lowest", x=0.397, y=0.315, size=9) +
  draw_label("2", x=0.365, y=0.2855, size=9) +
  draw_label("3", x=0.365, y=0.256, size=9) +
  draw_label("4", x=0.365, y=0.2265, size=9) +
  draw_label("5", x=0.365, y=0.197, size=9) + draw_label("highest", x=0.4, y=0.197, size=9) +
  draw_label("Experimental trial", x=0.39,y=0.1545,size=9) +
  draw_grob(circleGrob(x=0.345,y=0.125,r=0.007,gp=gpar(fill="black",col="transparent"))) +
  draw_label("Trial 1", x=0.38, y=0.125, size=9) +
  draw_image(triangle, scale=0.021, x=-0.155, y=-0.4045) +
  draw_label("Trial 2", x=0.38, y=0.0955, size=9)
  

ggsave2("FigureOutput/Fig1.pdf", width=9.7, height=6.45, units="in", device=cairo_pdf)
```


# Importing modelled parameter estimates from Mathematica
```{r}
model_delta_a <- read.csv("DataInput/ModelOutput_delta_a.csv") %>% 
  pivot_longer(cols=c(X0:X2), names_to = "timesEC50", values_to = "delta") %>% 
  rename("combo"=Combo)
model_delta_a$timesEC50 <- gsub("X", "", model_delta_a$timesEC50)

a_values <- model_delta_a %>% 
  select(combo, a) %>% 
  distinct() 



EC50s <-read.csv("DataInput/ModelOutput_EC50s.csv") 
avg_EC50s <- EC50s %>% 
  group_by(metal) %>% 
  summarise(avg_EC50=mean(EC50),
            se_EC50=std.error(EC50))
conc_times_avgEC50 <- avg_EC50s %>% 
  mutate(EC50_0 = avg_EC50*0,
         EC50_0.2 = avg_EC50*0.2,
         EC50_0.4 = avg_EC50*0.4,
         EC50_0.6 = avg_EC50*0.6,
         EC50_0.8 = avg_EC50*0.8,
         EC50_1.0 = avg_EC50*1,
         EC50_1.2 = avg_EC50*1.2,
         EC50_1.4 = avg_EC50*1.4,
         EC50_1.6 = avg_EC50*1.6,
         EC50_1.8 = avg_EC50*1.8,
         EC50_2 = avg_EC50*2) %>% 
  select(!c(se_EC50, EC50_0)) %>% 
  pivot_longer(cols=c(EC50_0.2:EC50_2), names_to = "times_EC50", values_to = "conc")
conc_times_avgEC50$times_EC50 <- gsub("EC50_","",conc_times_avgEC50$times_EC50)
```
###normality of a
```{r}
#all deltas calculated from each conc
hist(a_values$a, breaks=10,
     main=NULL, xlab="\u03b1")
qqnorm(a_values$a, pch = 1, frame = FALSE,
       main=NULL)
qqline(a_values$a, col = "steelblue", lwd = 2)

shapiro.test(a_values$a)
```
# Figure 3
##fig3A - strength of interactions by metal
###setting up data
```{r}
syn_ant_forward <- a_values %>% 
  mutate(metal = str_extract(combo, "^.{2}"),
         other_metal = str_extract(combo, ".{2}$"))
syn_ant_reverse <- a_values %>% 
  mutate(metal = str_extract(combo, ".{2}$"),
         other_metal = str_extract(combo, "^.{2}"))
syn_ant <- rbind(syn_ant_forward, syn_ant_reverse) %>% 
  rename(a_value = "a")

avg_syn_ant <- syn_ant %>%
  group_by(metal) %>% 
  summarize(avg_a = mean(a_value),
            se_a = std.error(a_value))

syn_ant$metal <- factor(levels = c("Mn", "Cu", "Ni", "Zn", "Cd", "Co"), syn_ant$metal)

syn_ant_dashed_lines <- syn_ant %>% 
  filter(metal=="Cd" & (other_metal=="Co" | other_metal=="Zn") |
           metal=="Co" & (other_metal=="Cd" | other_metal=="Zn") |
           metal=="Cu" & (other_metal=="Cd" | other_metal=="Co" | other_metal=="Zn") |
           metal=="Mn" & (other_metal=="Cd" | other_metal=="Co" | other_metal=="Zn") |
           metal=="Ni" & (other_metal=="Cd" | other_metal=="Co" | other_metal=="Zn") |
           metal=="Zn" & (other_metal=="Cd" | other_metal=="Co")) %>% 
  group_by(metal) %>% 
  summarise(avg_a = mean(a_value))
```
###graphing data
```{r}
fig3A <- syn_ant %>% 
  ggplot(aes(x=metal, y=a_value)) +
  geom_hline(yintercept = 0, color="grey80") +
  geom_vline(xintercept = 1.5) +
  geom_vline(xintercept = 2.5) +
  geom_vline(xintercept = 3.5) +
  geom_vline(xintercept = 4.5) +
  geom_vline(xintercept = 5.5) +
  geom_point(data=syn_ant, aes(x=metal, y=a_value, fill=combo, shape=other_metal, color=combo), size=6, stroke=2.5, position=position_dodge(width=0.7)) +
  geom_text(aes(label=other_metal, group=combo), position = position_dodge(0.7), size=3) +
  geom_point(data=avg_syn_ant, aes(x=metal, y=avg_a), size=5, shape=21, fill="white", color="black") +
  geom_segment(data=syn_ant_dashed_lines, aes(x=as.numeric(metal)-0.5, xend=as.numeric(metal)+0.5, y=avg_a, yend=avg_a), color="black", linetype = "dashed", linewidth=0.75) +
  scale_shape_manual(limits=c("Mn", "Cu", "Ni", "Zn", "Cd", "Co"), values = c(24, 25, 23, 22, 8, 21)) + 
  ylim(-3.3,3.3) +
  labs(x="Metal", y="a", color="Metal\ncombination", shape="\nOther metal") +
  scale_fill_manual(limits = c("CuMn", "MnZn", "MnNi", "CoMn", "CdMn", "CdNi", "NiZn", "CoNi", "CdZn", "CoZn", "CdCo", "CuNi", "CdCu", "CuZn", "CoCu"),
                     values = c("#55D0E6", "#D37AFF", "#FEB380", "#8A58D5", "#FE878B",   "#BB9B56","#FFC60C", "#2BA735", "#D48D8B", "#7282FF", "#9D8F8B",  "#CBDF1C", "#90B927",  "#3C99DB", "#3DC19D")) +
  scale_color_manual(limits = c("CuMn", "MnZn", "MnNi", "CoMn", "CdMn", "CdNi", "NiZn", "CoNi", "CdZn", "CoZn", "CdCo", "CuNi", "CdCu", "CuZn", "CoCu"),
                     values = c("#55D0E6", "#D37AFF", "#FEB380", "#8A58D5", "#FE878B",   "#BB9B56","#FFC60C", "#2BA735", "#D48D8B", "#7282FF", "#9D8F8B",  "#CBDF1C", "#90B927",  "#3C99DB", "#3DC19D")) +
  guides(fill="none", 
         color = guide_legend(override.aes = list(size=3), order=1),
         shape = guide_legend(order=2, override.aes = list(size=4, fill="black", stroke=1.5))) +
  theme_bw(base_size=14) +
  theme(panel.grid = element_blank(),
        axis.title = element_text(size=16, face="bold.italic", family="serif"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size=14, face="bold", color="black"),
        legend.box = "vertical",
        legend.spacing = unit(-0.2,"cm"),
        legend.text = element_text(size=9),
        legend.title=element_text(size=10),
        legend.key.size = unit(0.57,"cm"))
```
##Fig3_cowplot
```{r}
ggdraw() +
  draw_grob(rectGrob(gp=gpar(col="white", fill="white"))) +
  draw_plot(fig3A, width=0.87, height=1, x=0.13, y=0) +
  draw_grob(segmentsGrob(x0=0.07,y0=0.47,x1=0.07,y1=0.28, arrow=arrow(angle=20, length=unit(0.02, "npc"), ends="last", type="closed"), gp=gpar(fill="black",lwd=1.8))) +
  draw_grob(segmentsGrob(x0=0.07,y0=0.58,x1=0.07,y1=0.77, arrow=arrow(angle=20, length=unit(0.02, "npc"), ends="last", type="closed"), gp=gpar(fill="black",lwd=1.8))) +
  draw_label("Antagonistic \ntoxicity", x=0.07, y=0.825, size=12)+
  draw_label("Concentration \naddition", x=0.07, y=0.525, size=12)+
  draw_label("Synergistic \ntoxicity", x=0.07, y=0.225, size=12)
ggsave2("FigureOutput/Fig3.pdf", width=8,height=6,units="in")
```
# Figure 4 
##fig4A - avg obs d vs. a
```{r}
delta_a <- deltas_avg %>% 
  left_join(a_values, join_by(combo)) %>% 
  rename(a_value="a")
  

linear_mod <- lm(avg_delta ~ a_value, data=delta_a)
summary(linear_mod)

poly_model <- lm(avg_delta ~ poly(a_value, 2, raw=TRUE), data = delta_a)
summary(poly_model)
f <- function(x) (0.717 - (0.13878 * x) - (0.03644*x^2))

AIC(linear_mod)
AIC(poly_model)
BIC(linear_mod)
BIC(poly_model)

fig4A <- delta_a %>% 
  ggplot(aes(x=a_value, y=avg_delta)) +
  geom_hline(yintercept = 0, alpha=0.2) +
  geom_vline(xintercept = 0, alpha=0.2) +
  geom_smooth(method="lm", colour="black", se=F, size=0.7) +
  stat_function(fun=f, colour="blue", size=1) +
  geom_errorbar(aes(ymin=avg_delta-se_delta, ymax=avg_delta+se_delta), width=0.2) +
  geom_point(aes(color=combo), size=3) +
  labs(y="Observed \u03b4", x="a") +
  scale_color_manual(limits = c("CdCo", "CdZn", "CdMn", "MnNi", "CdNi", "CuNi", "CdCu", "CoNi", "CoCu", "CuMn", "CuZn", "CoZn", "CoMn", "MnZn", "NiZn"),
                     values = c("#9D8F8B", "#D48D8B", "#FE878B", "#FEB380", "#FFC60C", "#CBDF1C", "#90B927", "#2BA735", "#3DC19D", "#55D0E6", "#3C99DB", "#7282FF", "#8A58D5", "#D37AFF", "#BB9B56")) +
  scale_x_continuous(breaks=seq(-2, 3, 1)) +
  scale_y_continuous(breaks=seq(-0.5, 1, 0.5)) +
  theme_bw() +
  theme(
    aspect.ratio = 1,
    axis.title.y=element_text(face="bold"),
    axis.title.x=element_text(face="bold.italic", family="serif", size=15),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    legend.position = "none"
  )

# Adding another version with the legend so I can extract it later for the cowplot
fig4_legend <- delta_a %>% 
  ggplot(aes(x=a_value, y=avg_delta)) +
  geom_hline(yintercept = 0, alpha=0.2) +
  geom_vline(xintercept = 0, alpha=0.2) +
  geom_smooth(method="lm", colour="black", se=F, linewidth=0.7) +
  stat_function(fun=f, colour="blue", size=1) +
  geom_errorbar(aes(ymin=avg_delta-se_delta, ymax=avg_delta+se_delta), width=0.2) +
  geom_point(aes(color=combo), size=3) +
  labs(y="Observed \u03b4", x="a") +
  scale_color_manual(limits = c("CdCo", "CdZn", "CdMn", "MnNi", "CdNi", "CuNi", "CdCu", "CoNi", "CoCu", "CuMn", "CuZn", "CoZn", "CoMn", "MnZn", "NiZn"),
                     values = c("#9D8F8B", "#D48D8B", "#FE878B", "#FEB380", "#FFC60C", "#CBDF1C", "#90B927", "#2BA735", "#3DC19D", "#55D0E6", "#3C99DB", "#7282FF", "#8A58D5", "#D37AFF", "#BB9B56")) +
  scale_x_continuous(breaks=seq(-2, 3, 1)) +
  scale_y_continuous(breaks=seq(-0.5, 1, 0.5)) +
  theme_bw() +
  theme(
    aspect.ratio = 1,
    #axis.title.y=element_text(face="bold"),
    axis.title.x=element_text(face="bold.italic", family="serif", size=15),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    legend.position = "right"
  )
```

##fig4B - observed delta vs. modelled delta
```{r}
# these dstars are inferred using concentrations from each concentration level in the assay
dstar_conclevel <- read.csv("DataInput/dstar_predictions_conclevel.csv") %>%
  select(metal, conc, trial, obs_delta, exp_delta) %>% 
  group_by(metal, conc) %>% 
  summarise(obs_delta=mean(obs_delta),
            exp_delta=mean(exp_delta))

dstar_avg <- dstar_conclevel %>% 
  filter(conc!=5) %>% 
  group_by(metal) %>% 
  summarise(avg_obs_d = mean(obs_delta),
            se_obs_d = std.error(obs_delta),
            avg_exp_d = mean(exp_delta),
            se_exp_d = std.error(exp_delta))

#averaged across conc level 1-4
fig4B <- dstar_avg %>% 
  ggplot(aes(x=avg_exp_d, y=avg_obs_d)) +
  geom_hline(yintercept = 0, alpha=0.2) +
  geom_vline(xintercept = 0, alpha=0.2) +
  geom_abline(slope=1, linetype=3) +
  #geom_smooth(method="lm", colour="black", se=F, size=0.7) +
  geom_abline(slope=0.89621, intercept=-0.00352) +
  geom_errorbar(aes(ymin=avg_obs_d-se_obs_d, ymax=avg_obs_d+se_obs_d), width=0.05) +
  geom_errorbar(aes(xmin=avg_exp_d-se_exp_d, xmax=avg_exp_d+se_exp_d), width=0.05) +
  geom_point(aes(color=metal), size=3) +
  labs(y="Observed \u03b4", x="Inferred \u03b4*", color="Metal combo") +
  scale_color_manual(limits = c("CdCo", "CdZn", "CdMn", "MnNi", "CdNi", "CuNi", "CdCu", "CoNi", "CoCu", "CuMn", "CuZn", "CoZn", "CoMn", "MnZn", "NiZn"),
                     values = c("#9D8F8B", "#D48D8B", "#FE878B", "#FEB380", "#FFC60C", "#CBDF1C", "#90B927", "#2BA735", "#3DC19D", "#55D0E6", "#3C99DB", "#7282FF", "#8A58D5", "#D37AFF", "#BB9B56")) +
  scale_x_continuous(limits = c(-0.35,1.07), expand = c(0, 0), breaks = (c(0, 0.5, 1))) + 
  scale_y_continuous(limits = c(-0.35,1.07), expand = c(0, 0), breaks = (c(0, 0.5, 1))) +
  theme_bw() +
  theme(
    aspect.ratio = 1,
    axis.title=element_text(face="bold"),
    strip.background = element_blank(),
    strip.text.x = element_blank(),
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    legend.position = "none")

#DEMING REGRESSIONS
(sd(dstar_avg$avg_obs_d)^2)/(sd(dstar_avg$avg_exp_d)^2) #calculating error ratio
dem_reg(x="avg_exp_d", y="avg_obs_d", data=dstar_avg, error.ratio = 1.25)
```
##fig4C - inferred delta* over theoretical stressor gradient
```{r}
fig4C <- model_delta_a %>% 
  group_by(combo) %>% 
  ggplot(aes(x=as.numeric(timesEC50), y=delta, color=combo)) +
  geom_hline(yintercept = 0, alpha=0.75) +
  geom_vline(xintercept = 0, alpha=0.75) +
  geom_line(aes(color=combo), size=1) +
  labs(x="[metal]/EC50", y="Inferred \u03b4*", color="Metal\ncombo") +
  scale_color_manual(limits = c("CdCo", "CdZn", "CdMn", "MnNi", "CdNi", "CuNi", "CdCu", "CoNi", "CoCu", "CuMn", "CuZn", "CoZn", "CoMn", "MnZn", "NiZn"),
                     values = c("#9D8F8B", "#D48D8B", "#FE878B", "#FEB380", "#FFC60C", "#CBDF1C", "#90B927", "#2BA735", "#3DC19D", "#55D0E6", "#3C99DB", "#7282FF", "#8A58D5", "#D37AFF", "#BB9B56")) +
  theme_minimal() +
  theme(
    axis.title.y=element_text(face="bold"),
    axis.title.x=element_text(face="bold"),
    panel.grid.minor = element_blank(),
    plot.background = element_rect(fill="white", color=NA),
    legend.position = "none"
  ) 
```

##Fig4_cowplot
```{r}
legend_4 <- get_plot_component(fig4_legend, 'guide-box-right')
fig4top <- plot_grid(fig4A, fig4B, nrow = 1, labels = "AUTO") 
fig4bottom <- plot_grid(NULL,fig4C, NULL, nrow=1, labels = c(NULL, "C", NULL), rel_widths = c(0.2,1,0.2))
fig4component <- plot_grid(fig4top,fig4bottom, ncol=1, rel_heights = c(1,0.9))
plot_grid(fig4component, legend_4, nrow=1,rel_widths = c(1,0.1))


ggsave2("FigureOutput/Fig4.pdf", width=7.5,height=5,units="in", device=cairo_pdf)
```
# Figure 5
##loading prediction data and joining to observed interaction data
```{r}
predictions <- read.csv("DataInput/crosstol_predictions.csv") %>% 
  select(combo, prop.syn, all_slope, ORP) %>% 
  rename("ORP_diff" = ORP) %>% 
  distinct()

delta_a_predictions <- delta_a %>% left_join(predictions) %>% 
  mutate(ORP_sim = 0-ORP_diff)
```
##fig5 components
```{r}
# a vs. prop.syn
fig5A <- delta_a_predictions %>% 
  ggplot(aes(x=prop.syn, y=a_value, color=combo)) +
  geom_smooth(method="lm", color="black", fill="grey90") +
  geom_point(size=3) +
  scale_color_manual(values=combo_alphabet_palette) +
  scale_y_continuous(limits=c(-3,3.5), breaks=c(-3, -2, -1, 0, 1, 2, 3)) +
  theme_bw() +
  theme(panel.grid=element_blank(),
        legend.position = "none",
        axis.title=element_blank(),
        axis.text=element_blank())
lm(a_value ~ prop.syn, data=delta_a_predictions) %>% summary()

#a vs. allslope
fig5B <- delta_a_predictions %>% 
  ggplot(aes(x=all_slope, y=a_value, color=combo)) +
  geom_smooth(method="lm", color="black", fill="grey90", linetype=2) +
  geom_point(size=3) +
  scale_color_manual(values=combo_alphabet_palette) +
  scale_y_continuous(limits=c(-3,3.5), breaks=c(-3, -2, -1, 0, 1, 2, 3)) +
  theme_bw() +
  theme(panel.grid=element_blank(),
        legend.position = "none",
        axis.title=element_blank(),
        axis.text=element_blank())
lm(a_value ~ all_slope, data=delta_a_predictions) %>% summary()

#a vs. ORP_sim
fig5C <- delta_a_predictions %>% 
  ggplot(aes(x=ORP_sim, y=a_value, color=combo)) +
  geom_smooth(method="lm", color="black", fill="grey90") +
  geom_point(size=3) +
  scale_color_manual(values=combo_alphabet_palette) +
  scale_y_continuous(limits=c(-3,3.5), breaks=c(-3, -2, -1, 0, 1, 2, 3)) +
  labs(y="a") +
  theme_bw() +
  theme(panel.grid=element_blank(),
        legend.position = "none",
        axis.title.y=element_text(face="bold.italic", family="serif", size=15),
        axis.title.x=element_blank(),
        axis.text.x=element_blank())
lm(a_value ~ ORP_sim, data=delta_a_predictions) %>% summary()

#delta vs. prop.syn
fig5D <- delta_a_predictions %>% 
  ggplot(aes(x=prop.syn, y=avg_delta, color=combo)) +
  geom_smooth(method="lm", color="black", fill="grey80", linetype=2) +
  geom_point(size=3) +
  scale_color_manual(values=combo_alphabet_palette) +
  scale_y_continuous(limits=c(-0.21, 1.2)) +
  labs(x="Proportion of resistance genes\nwith same effect") +
  theme_bw() +
  theme(panel.grid=element_blank(),
        legend.position = "none",
        axis.title.y=element_blank(),
        axis.text.y=element_blank())
lm(avg_delta ~ prop.syn, data=delta_a_predictions) %>% summary()

#delta vs. allslope
fig5E <- delta_a_predictions %>% 
  ggplot(aes(x=all_slope, y=avg_delta, color=combo)) +
  geom_smooth(method="lm", color="black", fill="grey80", linetype=2) +
  geom_point(size=3) +
  scale_color_manual(values=combo_alphabet_palette) +
  scale_y_continuous(limits=c(-0.21, 1.2)) +
  labs(x="Correlation of concentration\nin soil/sediment samples") +
  theme_bw() +
  theme(panel.grid=element_blank(),
        legend.position = "none",
        axis.title.y=element_blank(),
        axis.text.y=element_blank())
lm(a_value ~ all_slope, data=delta_a_predictions) %>% summary()

#delta vs. ORP_sim
fig5F <- delta_a_predictions %>% 
  ggplot(aes(x=ORP_sim, y=avg_delta, color=combo)) +
  geom_smooth(method="lm", color="black", fill="grey80", linetype=2) +
  geom_point(size=3) +
  scale_color_manual(values=combo_alphabet_palette) +
  scale_y_continuous(limits=c(-0.21, 1.2)) +
  labs(x="Oxidation-reduction potential\nsimilarity", y="Observed \u03b4") +
  theme_bw() +
  theme(panel.grid=element_blank(),
        axis.title.y=element_text(face="bold"),
        legend.position = "none")

fig5_legend_component <- delta_a_predictions %>% 
  ggplot(aes(x=prop.syn, y=a_value, color=combo)) +
  geom_smooth(method="lm", color="black", fill="grey90") +
  geom_point(size=3) +
  scale_color_manual(values=combo_alphabet_palette) +
  scale_y_continuous(limits=c(-3,3.5), breaks=c(-3, -2, -1, 0, 1, 2, 3)) +
  labs(y="a", color="Metal \ncombination") +
  theme_bw() +
  theme(panel.grid=element_blank(),
        axis.title.y=element_text(face="bold.italic", family="serif", size=15),
        axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        legend.text = element_text(size=9),
        legend.title = element_text(size=10),
        legend.position = "right")
```

##Fig5_cowplot
```{r}
fig5_top <- plot_grid(fig5C, fig5A, fig5B, nrow = 1, rel_widths = c(1.15, 1, 1), labels = "AUTO", label_x = c(0.14,0.022,0.021), label_y = c(1.07,1.07,1.07))
fig5_bottom <- plot_grid(fig5F, fig5D, fig5E, nrow = 1, rel_widths = c(1.15, 1, 1), labels = c("D","E","F"), label_x = c(0.135,0.024,0.023), label_y = c(1.065,1.065,1.065))
fig5_plots<-plot_grid(NULL, fig5_top, NULL, fig5_bottom, ncol=1, rel_heights = c(0.05,1,0.05,1.17))

legend_5 <- get_plot_component(fig5_legend_component, 'guide-box-right')

fig5_legend <- plot_grid(NULL, legend_5, NULL, nrow = 3, rel_heights = c(1,1.5,1))

plot_grid(fig5_plots, fig5_legend, nrow = 1, rel_widths = c(1,0.1))
ggsave2("FigureOutput/Fig5.pdf", width = 9.6, height = 6.5, units = "in", dpi=700, device=cairo_pdf)
```
###Permutation test for a vs. prop.syn
```{r}
slopes_prop.syn <- data.frame(matrix(nrow = 1, ncol = 1)) %>% rename("slope"=matrix.nrow...1..ncol...1.)


for (i in seq(1:10000)) {
  delta_a_predictions$random_y <- sample(delta_a_predictions$a_value, replace=FALSE)
  
  my_lm <- lm(random_y ~ prop.syn, data=delta_a_predictions) 
  
  slopes_prop.syn[i,] <- summary(my_lm)$coefficients[2,1]
  }


slopes_prop.syn %>% filter(slope > 5.196) %>% nrow()
```
###Permutation test for a vs. ORP
```{r}
slopes_ORP <- data.frame(matrix(nrow = 1, ncol = 1)) %>% rename("slope"=matrix.nrow...1..ncol...1.)


for (i in seq(1:10000)) {
  delta_a_predictions$random_y <- sample(delta_a_predictions$a_value, replace=FALSE)
  
  my_lm <- lm(random_y ~ ORP_diff, data=delta_a_predictions) 
  
  slopes_ORP[i,] <- summary(my_lm)$coefficients[2,1]
  }


slopes_ORP %>% filter(slope < -78.8107) %>% nrow()
```

# Figure S2
```{r}
#example growth curves to demonstrate r
growthrates_trial1 <- max_growth1_wells %>% 
  mutate(trial="trial1")
growthrates_trial2 <- max_growth2_wells %>% 
  mutate(trial="trial2")
growthrates_all <- rbind(growthrates_trial1, growthrates_trial2) %>% 
  arrange(metal, maxSlope) 
growthrates_all_join <- growthrates_all %>% 
  select(trial, well, maxSlope)

growthcurves_trial1 <- df3_1 %>% 
  mutate(trial="trial1", .before = "t1")
growthcurves_trial2 <- df3_2 %>% 
  mutate(trial="trial2", .before = "t1")

old_cols_1dig <- paste("t", 1:9, sep = "")
new_cols_1dig <- paste("t", "00", 1:9, sep = "")
old_cols_2dig <- paste("t", 10:99, sep = "")
new_cols_2dig <- paste("t", "0", 10:99, sep = "")
growthcurves_all <- rbind(growthcurves_trial1, growthcurves_trial2) %>% 
  rename_with(~ new_cols_1dig[which(old_cols_1dig == .x)], .cols = old_cols_1dig) %>%
  rename_with(~ new_cols_2dig[which(old_cols_2dig == .x)], .cols = old_cols_2dig) %>% 
  left_join(growthrates_all_join, join_by(trial, well)) %>% 
  relocate(maxSlope,.after=trial) %>% 
  filter(metal=="YPAD" | metal=="Cd" | metal=="Co" | metal=="Cu" | metal=="Mn" | metal=="Ni" | metal=="Zn") %>% 
  arrange(metal,maxSlope)
```
```{r}
growthcurves_s3.2 <- growthcurves_all[c(160,161,162, 24,19,18,17,2, 56,52,51,47,42,35, 89,85,78,75,67, 117,115,112,108,101,96, 143,142,140,137,131,126, 200,193,190,186,178,174),] %>% 
  pivot_longer(cols = t001:t192, names_to = "timepoint", values_to = "OD") 

growthcurves_s3.2$metal <- factor(levels=c("YPAD","Cd","Co","Cu","Mn","Ni","Zn"), growthcurves_s3.2$metal)
growthcurves_s3.2$OD <- as.numeric(growthcurves_s3.2$OD)

growthcurves_s3.2 %>% 
  ggplot(aes(x=timepoint, y=OD)) +
  geom_smooth(aes(group=well, color=maxSlope), method="loess", span=0.1, se=F) + 
  scale_x_discrete(breaks=c("t048","t096","t144","t192"),
                   labels=c("12","24","36","48")) +
  scale_y_continuous(breaks = c(0.5, 1.0, 1.5)) + 
  scale_color_viridis(option="turbo", breaks=c(0.05, 0.1, 0.15, 0.2, 0.25, 0.3)) +
  labs(color="r",x="Time (hr)") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        legend.position = "top",
        legend.text = element_text(angle=0,vjust=0.5),
        legend.text.position = "top") +
  facet_wrap(~metal,nrow=1) +
  guides(color = guide_colorbar(barwidth = 15, barheight = 0.5))
ggsave("FigureOutput/FigS2.pdf", width=8, height=4, units="in")

#concentrations
s3.2_conc <- growthcurves_s3.2 %>% 
  select(-c(timepoint, OD)) %>% 
  distinct() %>% 
  arrange(metal, maxSlope) %>% 
  left_join(vgraph_mM)
```

# Figure S3 
##figS3A - all tolerance curves in one graph
```{r}
dose_response <- read.csv("DataInput/dose_response.csv")

dose_response %>%
  filter(conc!=0 & yeast!="BLANK" & media!="YPAD") %>% 
  group_by(media) %>% 
  ggplot(aes(x=mM, y=Mean, shape=as.character(trial))) +
  geom_rect(aes(ymin=0.003, ymax=0.029, xmin=-0.3, xmax=13.2), color="transparent", fill="grey90", alpha=0.25) + # neg control bar
  geom_rect(aes(ymin = 0.312, ymax=0.34, xmin=-0.3, xmax=13.2), color="transparent", fill="grey90", alpha=0.25) + # pos control bar
  geom_hline(yintercept = 0.25, color="grey90", linetype=1) +
  geom_hline(yintercept = 0.2, color="grey90", linetype=1) +
  geom_hline(yintercept = 0.15, color="grey90", linetype=1) +
  geom_hline(yintercept = 0.1, color="grey90", linetype=1) +
  geom_hline(yintercept = 0.05, color="grey90", linetype=1) +
  geom_path(size=1.5, aes(color=media)) +
  geom_point(size=3, shape=23, aes(fill=media)) +
  #geom_point(data=vgraph_Zn, aes(color=conc), size=5) +
  labs(x="Metal concentration (mM)", y="r", color="Metal", fill="Metal") +
  scale_color_manual(values=c("#FF9A17", "#3B83FF", "#3EFF38", "#FD73FF", "#FFD000",  "#A880FF")) +
  scale_fill_manual(values=c("#FF9A17", "#3B83FF", "#3EFF38", "#FD73FF", "#FFD000",  "#A880FF")) +
  scale_x_continuous(limits = c(-0.3,13.2), expand = c(0, 0)) + # width of graph on x scale, no margins
  scale_y_continuous(limits = c(0,0.35), expand = c(0, 0), breaks = (c(0.0,0.05,0.1,0.15,0.2,0.25,0.3,0.35))) +#height of graph on y, no margins, set ticks
  theme_bw(base_size = 13) +
  theme(legend.position="none",
        axis.title.y=element_text(face="italic"),
        panel.grid = element_blank())
ggsave("FigureOutput/FigS3/figS3A.jpg", width=11, height=3.7, units="in", dpi=700)
```
##fig3B-G - individual tolerance curves with fig1A growth rates overlaid
###getting growth rates from fig1A for overlay onto tolerance curves
```{r}
#getting growth rates from fig1A for overlay onto tolerance curves
vgraph_Cd <- combodata_avg %>% 
  filter(metal=="Cd") %>% 
  mutate(mM=case_when(trial=="two" & conc==1 ~ 0.005,
                      trial=="two" & conc==2 ~ 0.010,
                      trial=="two" & conc==3 ~ 0.016,
                      trial=="two" & conc==4 ~ 0.022,
                      trial=="two" & conc==5 ~ 0.027,
                      trial=="one" & conc==1 ~ 0.008,
                      trial=="one" & conc==2 ~ 0.011,
                      trial=="one" & conc==3 ~ 0.017,
                      trial=="one" & conc==4 ~ 0.026,
                      trial=="one" & conc==5 ~ 0.038)) %>% 
  rename(Mean="Mean_r")
vgraph_Co <- combodata_avg %>% 
  filter(metal=="Co") %>% 
  mutate(mM=case_when(trial=="two" & conc==1 ~ 0.5,
                      trial=="two" & conc==2 ~ 0.85,
                      trial=="two" & conc==3 ~ 0.9,
                      trial=="two" & conc==4 ~ 0.95,
                      trial=="two" & conc==5 ~ 1.3,
                      trial=="one" & conc==1 ~ 0.7,
                      trial=="one" & conc==2 ~ 0.86,
                      trial=="one" & conc==3 ~ 1,
                      trial=="one" & conc==4 ~ 1.32,
                      trial=="one" & conc==5 ~ 2.05)) %>% 
  rename(Mean="Mean_r")
vgraph_Cu <- combodata_avg %>% 
  filter(metal=="Cu") %>% 
  mutate(mM=case_when(trial=="two" & conc==1 ~ 4,
                      trial=="two" & conc==2 ~ 8.83,
                      trial=="two" & conc==3 ~ 10.17,
                      trial=="two" & conc==4 ~ 10.85,
                      trial=="two" & conc==5 ~ 12.9,
                      trial=="one" & conc==1 ~ 8.83,
                      trial=="one" & conc==2 ~ 10.17,
                      trial=="one" & conc==3 ~ 10.83,
                      trial=="one" & conc==4 ~ 12.00,
                      trial=="one" & conc==5 ~ 13.5)) %>% 
  rename(Mean="Mean_r")
vgraph_Mn <- combodata_avg %>% 
  filter(metal=="Mn") %>% 
  mutate(mM=case_when(trial=="two" & conc==1 ~ 0.85,
                      trial=="two" & conc==2 ~ 1,
                      trial=="two" & conc==3 ~ 1.14,
                      trial=="two" & conc==4 ~ 1.25,
                      trial=="two" & conc==5 ~ 1.6,
                      trial=="one" & conc==1 ~ 0.86,
                      trial=="one" & conc==2 ~ 1.14,
                      trial=="one" & conc==3 ~ 1.31,
                      trial=="one" & conc==4 ~ 1.66,
                      trial=="one" & conc==5 ~ 2.23,)) %>% 
  rename(Mean="Mean_r")
vgraph_Ni <- combodata_avg %>% 
  filter(metal=="Ni") %>% 
  mutate(mM=case_when(trial=="two" & conc==1 ~ 2.3,
                      trial=="two" & conc==2 ~ 2.6,
                      trial=="two" & conc==3 ~ 2.75,
                      trial=="two" & conc==4 ~ 3,
                      trial=="two" & conc==5 ~ 3.2,
                      trial=="one" & conc==1 ~ 1.88,
                      trial=="one" & conc==2 ~ 2.4,
                      trial=="one" & conc==3 ~ 3,
                      trial=="one" & conc==4 ~ 3.6,
                      trial=="one" & conc==5 ~ 5.1)) %>% 
  rename(Mean="Mean_r")
vgraph_Zn <- combodata_avg %>% 
  filter(metal=="Zn") %>% 
  mutate(mM=case_when(trial=="two" & conc==1 ~ 3.33,
                      trial=="two" & conc==2 ~ 4,
                      trial=="two" & conc==3 ~ 4.8,
                      trial=="two" & conc==4 ~ 5.4,
                      trial=="two" & conc==5 ~ 6,
                      trial=="one" & conc==1 ~ 4,
                      trial=="one" & conc==2 ~ 4.74,
                      trial=="one" & conc==3 ~ 5.4,
                      trial=="one" & conc==4 ~ 6,
                      trial=="one" & conc==5 ~ 6.6)) %>% 
  rename(Mean="Mean_r")
```
###overlaying growth rates on tolerance curves
```{r}
dose_response %>%
  filter(media=="Cd" & conc!=0 & yeast!="BLANK") %>% # Cadmium media with yeast
  ggplot(aes(x=mM, y=Mean, shape=as.character(trial))) + # set axes and aesthetics
  geom_rect(aes(ymin =0, ymax=0.029, xmin=0, xmax=0.055), fill="grey90", alpha=0.25) + # neg control bar (Cd blanks)
  geom_rect(aes(ymin = 0.312, ymax=0.34, xmin=0, xmax=0.055), fill="grey90", alpha=0.25) + # pos control bar
  geom_hline(yintercept = 0.25, color="#AAAAAA", linetype=1) +
  geom_hline(yintercept = 0.2, color="#888888", linetype=1) +
  geom_hline(yintercept = 0.15, color="#666666", linetype=1) +
  geom_hline(yintercept = 0.1, color="#434343", linetype=1) +
  geom_hline(yintercept = 0.05, color="#212121", linetype=1) +
  geom_path(color="#FF9A17", size=2.5, alpha=0.25) + # tolerance curve lines
  geom_point(fill="#FF9A17", size=5, shape=23, alpha=0.25) + # tolerance curve points
  geom_point(data=vgraph_Cd, aes(color=conc), size=6) + # vgraph points
  scale_shape_manual(values = c(11, 9, 19,17)) + 
  labs(x="Cadmium concentration (mM)", y="r") + # axis labels
  scale_color_manual(values=bw_palette_5conc) + # vgraph point colors
  scale_x_continuous(limits = c(0,0.055), expand = c(0, 0)) + # width of graph on x scale, no margins
  scale_y_continuous(limits = c(0,0.35), expand = c(0, 0), breaks = (c(0.0,0.05,0.1,0.15,0.2,0.25,0.3,0.35))) +#height of graph on y, no margins, set ticks
  theme_bw(base_size = 15) + 
  theme(legend.position="none", # remove legend
        axis.title.y=element_text(face="italic"), # italicize y axis title
        panel.grid = element_blank()) # white panel background
ggsave("FigureOutput/FigS3/figS3B.jpg", width=5, height=3.7, units="in", dpi=700)

dose_response %>%
  filter(media=="Co"& conc!=0 & yeast!="BLANK") %>% 
  ggplot(aes(x=mM, y=Mean, shape=as.character(trial))) +
  geom_rect(aes(ymin =0, ymax=0.029, xmin=0, xmax=3.5), fill="grey90", alpha=0.25) + # neg control bar (Cd blanks)
  geom_rect(aes(ymin = 0.312, ymax=0.34, xmin=0, xmax=3.5), fill="grey90", alpha=0.25) + # pos control bar
  geom_hline(yintercept = 0.25, color="#AAAAAA", linetype=1) +
  geom_hline(yintercept = 0.2, color="#888888", linetype=1) +
  geom_hline(yintercept = 0.15, color="#666666", linetype=1) +
  geom_hline(yintercept = 0.1, color="#434343", linetype=1) +
  geom_hline(yintercept = 0.05, color="#212121", linetype=1) +
  geom_path(color="#3B83FF", size=2.5, alpha=0.25) + 
  geom_point(fill="#3B83FF", size=5, shape=23, alpha=0.25) + 
  geom_point(data=vgraph_Co, aes(color=conc), size=6) +
  scale_shape_manual(values = c(10, 11, 9, 19, 17)) + 
  labs(x="Cobalt concentration (mM)", y="r") +
  scale_color_manual(values=bw_palette_5conc) +
  scale_x_continuous(limits = c(0, 3.5), expand = c(0, 0)) + # width of graph on x scale, no margins
  scale_y_continuous(limits = c(0, 0.35), expand = c(0, 0), breaks = (c(0.0,0.05,0.1,0.15,0.2,0.25,0.3,0.35))) +#height of graph on y, no margins, set ticks
  theme_bw(base_size = 15) +
  theme(legend.position="none",
        axis.title.y=element_text(face="italic"),
        panel.grid = element_blank())
ggsave("FigureOutput/FigS3/figS3C.jpg", width=5, height=3.7, units="in", dpi=700)

dose_response %>%
  filter(media=="Cu"& conc!=0 & yeast!="BLANK") %>% 
  ggplot(aes(x=mM, y=Mean, shape=as.character(trial))) +
  geom_rect(aes(ymin =0, ymax=0.029, xmin=0, xmax=15.5), fill="grey90", alpha=0.25) + # neg control bar (Cd blanks)
  geom_rect(aes(ymin = 0.312, ymax=0.34, xmin=0, xmax=15.5), fill="grey90", alpha=0.25) + # pos control bar
  geom_hline(yintercept = 0.25, color="#AAAAAA", linetype=1) +
  geom_hline(yintercept = 0.2, color="#888888", linetype=1) +
  geom_hline(yintercept = 0.15, color="#666666", linetype=1) +
  geom_hline(yintercept = 0.1, color="#434343", linetype=1) +
  geom_hline(yintercept = 0.05, color="#212121", linetype=1) +
  geom_path(color="#3EFF38", size=2.5, alpha=0.25) + 
  geom_point(fill="#3EFF38", size=5, shape=23, alpha=0.25) + 
  geom_point(data=vgraph_Cu, aes(color=conc), size=6) +
  scale_shape_manual(values = c(10, 11, 9, 19, 17)) + 
  labs(x="Copper concentration (mM)", y="r") +
  scale_color_manual(values=bw_palette_5conc) +
  scale_x_continuous(limits = c(0,15.5), expand = c(0, 0), breaks = (c(0.0,2,4,6,8,10,12,14))) +
  scale_y_continuous(limits = c(0,0.35), expand = c(0, 0), breaks = (c(0.0,0.05,0.1,0.15,0.2,0.25,0.3,0.35))) +
  theme_bw(base_size = 15) +
  theme(legend.position="none",
        axis.title.y=element_text(face="italic"),
        panel.grid = element_blank())
ggsave("FigureOutput/FigS3/figS3D.jpg", width=5, height=3.7, units="in", dpi=700)

dose_response %>%
  filter(media=="Mn"& conc!=0 & yeast!="BLANK") %>% 
  ggplot(aes(x=mM, y=Mean, shape=as.character(trial))) +
  geom_rect(aes(ymin =0, ymax=0.029, xmin=0, xmax=4.9), fill="grey90", alpha=0.25) + 
  geom_rect(aes(ymin = 0.312, ymax=0.34, xmin=0, xmax=4.9), fill="grey90", alpha=0.25) + 
  geom_hline(yintercept = 0.25, color="#AAAAAA", linetype=1) +
  geom_hline(yintercept = 0.2, color="#888888", linetype=1) +
  geom_hline(yintercept = 0.15, color="#666666", linetype=1) +
  geom_hline(yintercept = 0.1, color="#434343", linetype=1) +
  geom_hline(yintercept = 0.05, color="#212121", linetype=1) +
  geom_path(color="#FD73FF", size=2.5, alpha=0.25) + 
  geom_point(fill="#FD73FF", size=5, shape=23, alpha=0.25) + 
  geom_point(data=vgraph_Mn, aes(color=conc), size=6) +
  scale_shape_manual(values = c(10, 11, 19, 17, 9)) + 
  labs(x="Manganese concentration (mM)", y="r") +
  scale_color_manual(values=bw_palette_5conc) +
  scale_x_continuous(limits = c(0,4.9), expand = c(0, 0)) + 
  scale_y_continuous(limits = c(0,0.35), expand = c(0, 0), breaks = (c(0.0,0.05,0.1,0.15,0.2,0.25,0.3,0.35))) +
  theme_bw(base_size = 15) +
  theme(legend.position="none",
        axis.title.y=element_text(face="italic"),
        panel.grid = element_blank())
ggsave("FigureOutput/FigS3/figS3E.jpg", width=5, height=3.7, units="in", dpi=700)

dose_response %>%
  filter(media=="Ni"& conc!=0 & yeast!="BLANK") %>% 
  ggplot(aes(x=mM, y=Mean, shape=as.character(trial))) +
  geom_rect(aes(ymin =0, ymax=0.029, xmin=0, xmax=4.5), fill="grey90", alpha=0.25) + 
  geom_rect(aes(ymin = 0.312, ymax=0.34, xmin=0, xmax=4.5), fill="grey90", alpha=0.25) + 
  geom_hline(yintercept = 0.25, color="#AAAAAA", linetype=1) +
  geom_hline(yintercept = 0.2, color="#888888", linetype=1) +
  geom_hline(yintercept = 0.15, color="#666666", linetype=1) +
  geom_hline(yintercept = 0.1, color="#434343", linetype=1) +
  geom_hline(yintercept = 0.05, color="#212121", linetype=1) +
  geom_path(color="#ffd000", size=2.5, alpha=0.25) + 
  geom_point(fill="#ffd000", size=5, shape=23, alpha=0.25) + 
  geom_point(data=vgraph_Ni, aes(color=conc), size=6) +
  scale_shape_manual(values = c(10, 11, 9, 19, 17)) + 
  labs(x="Nickel concentration (mM)", y="r") +
  scale_color_manual(values=bw_palette_5conc) +
  scale_x_continuous(limits = c(0,4.5), expand = c(0, 0)) +
  scale_y_continuous(limits = c(0,0.35), expand = c(0, 0), breaks = (c(0.0,0.05,0.1,0.15,0.2,0.25,0.3,0.35))) +
  theme_bw(base_size = 15) +
  theme(legend.position="none",
        axis.title.y=element_text(face="italic"),
        panel.grid = element_blank())
ggsave("FigureOutput/FigS3/figS3F.jpg", width=5, height=3.7, units="in", dpi=700)

dose_response %>%
  filter(media=="Zn"& conc!=0 & yeast!="BLANK") %>% 
  ggplot(aes(x=mM, y=Mean, shape=as.character(trial))) +
  geom_rect(aes(ymin =0, ymax=0.029, xmin=0, xmax=8.7), fill="grey90", alpha=0.25) + 
  geom_rect(aes(ymin = 0.312, ymax=0.34, xmin=0, xmax=8.7), fill="grey90", alpha=0.25) + 
  geom_hline(yintercept = 0.25, color="#AAAAAA", linetype=1) +
  geom_hline(yintercept = 0.2, color="#888888", linetype=1) +
  geom_hline(yintercept = 0.15, color="#666666", linetype=1) +
  geom_hline(yintercept = 0.1, color="#434343", linetype=1) +
  geom_hline(yintercept = 0.05, color="#212121", linetype=1) +
  geom_path(color="#A880FF", size=2.5, alpha=0.25) + 
  geom_point(fill="#A880FF", size=5, shape=23, alpha=0.25) + 
  geom_point(data=vgraph_Zn, aes(color=conc), size=6) +
  scale_shape_manual(values = c(10, 11, 9, 19, 17)) + 
  labs(x="Zinc concentration (mM)", y="r") +
  scale_color_manual(values=bw_palette_5conc) +
  scale_x_continuous(limits = c(0,8.7), expand = c(0, 0)) + 
  scale_y_continuous(limits = c(0,0.35), expand = c(0, 0), breaks = (c(0.0,0.05,0.1,0.15,0.2,0.25,0.3,0.35))) +
  theme_bw(base_size = 15) +
  theme(legend.position="none",
        axis.title.y=element_text(face="italic"),
        panel.grid = element_blank())
ggsave("FigureOutput/FigS3/figS3G.jpg", width=5, height=3.7, units="in", dpi=700)
```
##figS3H - difference from target
```{r}
mydata <- rbind(vgraph_Cd, vgraph_Co, vgraph_Cu, vgraph_Mn, vgraph_Ni, vgraph_Zn) %>% 
  mutate(yeast="OLY077")

# Define target values
targets <- c("1" = 0.25, "2" = 0.2, "3" = 0.15, "4" = 0.1, "5" = 0.05)

# Add target values to the dataset
mydata$target <- targets[as.character(mydata$conc)]
mydata <- mydata %>% mutate(difference=Mean-target)
great_diff <- mydata %>% filter(difference > 0.05) %>% arrange(metal, conc, trial)

mydata %>% 
  ggplot(aes(x=conc,y=difference, fill=metal, shape=as.character(trial))) +
   annotate("rect", xmin=0.5, xmax=1.5, ymin=-0.15, ymax=0.2, alpha=0.25, fill="#AAAAAA") +
  annotate("rect", xmin=1.5, xmax=2.5, ymin=-0.15, ymax=0.2, alpha=0.25, fill="#888888") +
  annotate("rect", xmin=2.5, xmax=3.5, ymin=-0.15, ymax=0.2, alpha=0.25, fill="#666666") +
  annotate("rect", xmin=3.5, xmax=4.5, ymin=-0.15, ymax=0.2, alpha=0.25, fill="#434343") +
  annotate("rect", xmin=4.5, xmax=5.5, ymin=-0.15, ymax=0.2, alpha=0.25, fill="#212121") +
  geom_hline(yintercept = 0) +
  geom_point(position = position_dodge(width=0.7), size=5) +
  labs(x="Concentration level (Target r)", y="Observed r - Target r") +
  scale_fill_manual(values=c("#FF9A17", "#3B83FF", "#3EFF38", "#FD73FF", "#FFD000",  "#A880FF")) +
  scale_shape_manual(values=c(21,24)) +
  scale_y_continuous(limits = c(-0.15,0.2), expand = c(0, 0)) +
  scale_x_discrete(labels=c("1" = "1 (0.25)", "2" = "2 (0.20)", "3" = "3 (0.15)", "4" = "4 (0.10)", "5" = "5 (0.05)")) +
  theme_bw(base_size=14) +
  theme(legend.position="none")
```
###confint stat for diff from target
```{r}
options(digits=3)
combodata_unavg %>% arrange(metal, conc, trial, replicate) %>% View()

#C1 target m: 0.25
Cd_C1 <- combodata_unavg %>% filter(metal=="Cd" & conc==1)
t.test(Cd_C1$maxSlope) # 0.255 0.294      outside target
#C2 target m: 0.20
Cd_C2 <- combodata_unavg %>% filter(metal=="Cd" & conc==2)
t.test(Cd_C2$maxSlope) # 0.224 0.283      oustide target
#C3 target m: 0.15
Cd_C3 <- combodata_unavg %>% filter(metal=="Cd" & conc==3)
t.test(Cd_C3$maxSlope) # 0.215 0.232      outside target
#C4 target m: 0.10
Cd_C4 <- combodata_unavg %>% filter(metal=="Cd" & conc==4)
t.test(Cd_C4$maxSlope) # 0.0901 0.1057    
#C5 target m: 0.05
Cd_C5 <- combodata_unavg %>% filter(metal=="Cd" & conc==5)
t.test(Cd_C5$maxSlope) # 0.00672 0.05547  


#C1 target m: 0.25
Co_C1 <- combodata_unavg %>% filter(metal=="Co" & conc==1)
t.test(Co_C1$maxSlope) # 0.261 0.289      outside target
#C2 target m: 0.20
Co_C2 <- combodata_unavg %>% filter(metal=="Co" & conc==2)
t.test(Co_C2$maxSlope) # 0.185 0.268      
#C3 target m: 0.15
Co_C3 <- combodata_unavg %>% filter(metal=="Co" & conc==3)
t.test(Co_C3$maxSlope) # 0.104 0.146      outside target
#C4 target m: 0.10
Co_C4 <- combodata_unavg %>% filter(metal=="Co" & conc==4)
t.test(Co_C4$maxSlope) # 0.0901 0.1057
#C5 target m: 0.05
Co_C5 <- combodata_unavg %>% filter(metal=="Co" & conc==5)
t.test(Co_C5$maxSlope) # 0.00672 0.05547


#C1 target m: 0.25
Cu_C1 <- combodata_unavg %>% filter(metal=="Cu" & conc==1)
t.test(Cu_C1$maxSlope) # 0.184 0.285     
#C2 target m: 0.20
Cu_C2 <- combodata_unavg %>% filter(metal=="Cu" & conc==2)
t.test(Cu_C2$maxSlope) # 0.169 0.224      
#C3 target m: 0.15
Cu_C3 <- combodata_unavg %>% filter(metal=="Cu" & conc==3)
t.test(Cu_C3$maxSlope) # 0.0935 0.1878    
#C4 target m: 0.10
Cu_C4 <- combodata_unavg %>% filter(metal=="Cu" & conc==4)
t.test(Cu_C4$maxSlope) # 0.122 0.213      outside target
#C5 target m: 0.05
Cu_C5 <- combodata_unavg %>% filter(metal=="Cu" & conc==5)
t.test(Cu_C5$maxSlope) # -0.0107  0.0441  outside target


#C1 target m: 0.25
Mn_C1 <- combodata_unavg %>% filter(metal=="Mn" & conc==1)
t.test(Mn_C1$maxSlope) # 0.246 0.319     
#C2 target m: 0.20
Mn_C2 <- combodata_unavg %>% filter(metal=="Mn" & conc==2)
t.test(Mn_C2$maxSlope) # 0.182 0.207     
#C3 target m: 0.15
Mn_C3 <- combodata_unavg %>% filter(metal=="Mn" & conc==3)
t.test(Mn_C3$maxSlope) # 0.103 0.159    
#C4 target m: 0.10
Mn_C4 <- combodata_unavg %>% filter(metal=="Mn" & conc==4)
t.test(Mn_C4$maxSlope) # 0.0649 0.1103     
#C5 target m: 0.05
Mn_C5 <- combodata_unavg %>% filter(metal=="Mn" & conc==5)
t.test(Mn_C5$maxSlope) # 0.0404 0.0646 


#C1 target m: 0.25
Ni_C1 <- combodata_unavg %>% filter(metal=="Ni" & conc==1)
t.test(Ni_C1$maxSlope) # 0.318 0.347      outside target    
#C2 target m: 0.20
Ni_C2 <- combodata_unavg %>% filter(metal=="Ni" & conc==2)
t.test(Ni_C2$maxSlope) # 0.275 0.311      outside target
#C3 target m: 0.15
Ni_C3 <- combodata_unavg %>% filter(metal=="Ni" & conc==3)
t.test(Ni_C3$maxSlope) # 0.0916 0.1941   
#C4 target m: 0.10
Ni_C4 <- combodata_unavg %>% filter(metal=="Ni" & conc==4)
t.test(Ni_C4$maxSlope) # 0.0654 0.1028    
#C5 target m: 0.05
Ni_C5 <- combodata_unavg %>% filter(metal=="Ni" & conc==5)
t.test(Ni_C5$maxSlope) # 0.0319 0.0549


#C1 target m: 0.25
Zn_C1 <- combodata_unavg %>% filter(metal=="Zn" & conc==1)
t.test(Zn_C1$maxSlope) # 0.232 0.254      
#C2 target m: 0.20
Zn_C2 <- combodata_unavg %>% filter(metal=="Zn" & conc==2)
t.test(Zn_C2$maxSlope) # 0.201 0.225      
#C3 target m: 0.15
Zn_C3 <- combodata_unavg %>% filter(metal=="Zn" & conc==3)
t.test(Zn_C3$maxSlope) # 0.142 0.181   
#C4 target m: 0.10
Zn_C4 <- combodata_unavg %>% filter(metal=="Zn" & conc==4)
t.test(Zn_C4$maxSlope) # 0.095 0.109    
#C5 target m: 0.05
Zn_C5 <- combodata_unavg %>% filter(metal=="Zn" & conc==5)
t.test(Zn_C5$maxSlope) # 0.0324 0.0616
```
#Figure S4
## figS4A - EC50 numline
```{r}
#Values here are from Mathematica estimates of EC50 from single metal dose response curves
single_EC50s <- data.frame(
  metal=c("Cd","Co","Cu","Mn","Ni","Zn"),
  EC50=c(0.01927709305337785,0.9193242167751756,10.547323688456077,1.141893553606749,2.8313242497197466,4.866965299472917)) %>% 
  mutate(numline="yes")
single_EC50s %>%  
  ggplot(aes(x=numline,y=EC50, color=metal)) +
  geom_point(size=6) +
  scale_color_manual(values=single_palette) +
  #scale_x_discrete(expand = c(0,0)) +
  labs(x="Metal", y="EC50 (mM)", color="Metal") +
  theme_bw(base_size=12) +
  theme(panel.grid = element_blank(),
        axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = "top") +
  coord_flip() +
  guides(colour = guide_legend(nrow = 1))
```
##figS4B - EC50 and SI overlaid on dose-response curve
```{r}
my_fn <- function(max,c,EC50,beta) {
  max / (1 + (c / EC50)^beta)
}

functions <- data.frame(metal = c("Cd", "Co", "Cu", "Mn" ,"Ni", "Zn"),
                        max = c(0.320975,0.324288,0.308914,0.33055,0.3332,0.323794),
                        EC50 = c(0.019277,0.919324,10.54732,1.14189,2.831324,4.866965),
                        beta = c(2.372425,4.681064,5.846534,4.37898,11.62968,4.579189),
                        r = c(0.25, 0))

r_values <- c(0.25, 0.2, 0.15, 0.1, 0.05)
conc_level_values <- c(1,2,3,4,5)

functions_expanded <- functions %>%
  slice(rep(1:n(), each = length(r_values))) %>%
  mutate(r = rep(r_values, times = nrow(functions)),
         conc_level= rep(conc_level_values, times = nrow(functions))) %>%
  mutate(mM=(-EC50^beta + (EC50^beta*max)/r)^(1/beta))

#functions_expanded %>% write.csv("modelled_conclevel_mM_eq2.csv")

Cd_labels <- data.frame(
  x = c(0,0.00378,0.00755,0.01133,0.01511,0.01889,0.02266,0.02644,0.03022,0.03400,0.00378,0.00755,0.01133,0.01511,0.01889,0.02266,0.02644,0.03022,0.03400),
  label = c("0","0.004","0.008","0.011","0.015","0.019","0.023","0.026","0.030","0.034","\n0.2","\n0.4","\n0.6","\n0.8","\n1.0","\n1.2","\n1.4","\n1.6","\n1.8"))
S4B1 <- vgraph_Cd %>%
  ggplot(aes(x=mM, y=Mean, shape=as.character(trial), color=conc)) +
  geom_rect(aes(ymin =0, ymax=0.029, xmin=0, xmax=0.038), fill="grey90", color="transparent", alpha=0.25) + 
  geom_rect(aes(ymin = 0.312, ymax=0.34, xmin=0, xmax=0.038), fill="grey90", color="transparent", alpha=0.25) + 
  geom_vline(xintercept = 0.00378, linetype=3) + #mM of EC50 times 0.2
  geom_vline(xintercept = 0.00755, linetype=3) + #mM of EC50 times 0.4
  geom_vline(xintercept = 0.01133, linetype=3) + #mM of EC50 times 0.6
  geom_vline(xintercept = 0.01511, linetype=3) + #mM of EC50 times 0.8
  geom_vline(xintercept = 0.01889, size=2, color="#FF9A17") + #mM of EC50 times 1
  geom_vline(xintercept = 0.02266, linetype=3) + #mM of EC50 times 1.2
  geom_vline(xintercept = 0.02644, linetype=3) + #mM of EC50 times 1.4
  geom_vline(xintercept = 0.03022, linetype=3) + #mM of EC50 times 1.6
  geom_vline(xintercept = 0.03400, linetype=3) + #mM of EC50 times 1.8
  geom_function(fun = ~ my_fn(max=0.320975, c=.x, EC50=0.019277, beta=2.372425)) +
  geom_point(size=4.5) +
  labs(x="Metal Concentration (mM)\nStressor Instensity (x*EC50)", y="m") +
  scale_color_manual(values=bw_palette_5conc) +
  scale_x_continuous(limits = c(0,0.038), 
                     expand = c(0, 0),
                     breaks = Cd_labels$x,
                     labels = Cd_labels$label,
                     minor_breaks = NULL) + 
  scale_y_continuous(limits = c(0,0.34), expand = c(0, 0), breaks = (c(0.0,0.05,0.1,0.15,0.2,0.25,0.3))) +
  theme_bw(base_size = 13) + 
  theme(legend.position="none", # remove legend
        axis.title = element_blank(),
        panel.grid = element_blank()) # white panel background

Co_labels <- data.frame(
  x = c(0,0.18280,0.36559,0.54839,0.73119,0.91398,1.09678,1.27958,1.46237,1.64517,0.18280,0.36559,0.54839,0.73119,0.91398,1.09678,1.27958,1.46237,1.64517),
  label = c("0","0.18","0.37","0.55","0.73","0.91","1.10","1.28","1.46","1.65","\n0.2","\n0.4","\n0.6","\n0.8","\n1.0","\n1.2","\n1.4","\n1.6","\n1.8"))
S4B2 <- vgraph_Co %>%
  ggplot(aes(x=mM, y=Mean, shape=as.character(trial), color=conc)) +
  geom_rect(aes(ymin =0, ymax=0.029, xmin=0, xmax=1.83), fill="grey90", color="transparent", alpha=0.25) + 
  geom_rect(aes(ymin = 0.312, ymax=0.34, xmin=0, xmax=1.83), fill="grey90", color="transparent", alpha=0.25) + 
  geom_vline(xintercept = 0.18280, linetype=3) + #mM of EC50 times 0.2
  geom_vline(xintercept = 0.36559, linetype=3) + #mM of EC50 times 0.4
  geom_vline(xintercept = 0.54839, linetype=3) + #mM of EC50 times 0.6
  geom_vline(xintercept = 0.73119, linetype=3) + #mM of EC50 times 0.8
  geom_vline(xintercept = 0.91398, size=2, color="#3B83FF") + #mM of EC50 times 1
  geom_vline(xintercept = 1.09678, linetype=3) + #mM of EC50 times 1.2
  geom_vline(xintercept = 1.27958, linetype=3) + #mM of EC50 times 1.4
  geom_vline(xintercept = 1.46237, linetype=3) + #mM of EC50 times 1.6
  geom_vline(xintercept = 1.64517, linetype=3) + #mM of EC50 times 1.8
  geom_function(fun = ~ my_fn(max=0.324288, c=.x, EC50=0.919324, beta=4.681064)) +
  geom_point(size=4.5) +
  labs(x="Metal Concentration (mM)\nStressor Instensity (x*EC50)", y="m") +
  scale_color_manual(values=bw_palette_5conc) +
  scale_x_continuous(limits = c(0,1.83), 
                     expand = c(0, 0),
                     breaks = Co_labels$x,
                     labels = Co_labels$label,
                     minor_breaks = NULL) + 
  scale_y_continuous(limits = c(0, 0.34), expand = c(0, 0), breaks = (c(0.0,0.05,0.1,0.15,0.2,0.25,0.3))) +#height of graph on y, no margins, set ticks
  theme_bw(base_size = 13) +
  theme(legend.position="none",
        axis.title = element_blank(),
        axis.text.y = element_blank(),
        panel.grid = element_blank())

Cu_labels <- data.frame(
  x = c(0,2.04472,4.08944,6.13416,8.17887,10.22359,12.26831,14.31303,16.35775,18.40247,2.04472,4.08944,6.13416,8.17887,10.22359,12.26831,14.31303,16.35775,18.40247),
  label = c("0","2.04","4.09","6.13","8.18","10.22","12.27","14.31","16.36","18.40","\n0.2","\n0.4","\n0.6","\n0.8","\n1.0","\n1.2","\n1.4","\n1.6","\n1.8"))
S4B3 <- vgraph_Cu %>%
  ggplot(aes(x=mM, y=Mean, shape=as.character(trial), color=conc)) +
  geom_rect(aes(ymin =0, ymax=0.029, xmin=0, xmax=20.45), fill="grey90", color="transparent", alpha=0.25) + 
  geom_rect(aes(ymin = 0.312, ymax=0.34, xmin=0, xmax=20.45), fill="grey90", color="transparent", alpha=0.25) + 
  geom_vline(xintercept = 2.04472, linetype=3) + #mM of EC50 times 0.2
  geom_vline(xintercept = 4.08944, linetype=3) + #mM of EC50 times 0.4
  geom_vline(xintercept = 6.13416, linetype=3) + #mM of EC50 times 0.6
  geom_vline(xintercept = 8.17887, linetype=3) + #mM of EC50 times 0.8
  geom_vline(xintercept = 10.22359, size=2, color="#3EFF38") + #mM of EC50 times 1
  geom_vline(xintercept = 12.26831, linetype=3) + #mM of EC50 times 1.2
  geom_vline(xintercept = 14.31303, linetype=3) + #mM of EC50 times 1.4
  geom_vline(xintercept = 16.35775, linetype=3) + #mM of EC50 times 1.6
  geom_vline(xintercept = 18.40247, linetype=3) + #mM of EC50 times 1.8
  geom_function(fun = ~ my_fn(max=0.308914, c=.x, EC50=10.54732, beta=5.846534)) +
  geom_point(size=4.5) +
  labs(x="Metal Concentration (mM)\nStressor Instensity (x*EC50)", y="m") +
  scale_color_manual(values=bw_palette_5conc) +
  scale_x_continuous(limits = c(0,20.45), 
                     expand = c(0, 0),
                     breaks = Cu_labels$x,
                     labels = Cu_labels$label,
                     minor_breaks = NULL) + 
  scale_y_continuous(limits = c(0,0.34), expand = c(0, 0), breaks = (c(0.0,0.05,0.1,0.15,0.2,0.25,0.3))) +
  theme_bw(base_size = 13) +
  theme(legend.position="none",
        axis.title = element_blank(),
        axis.text.y = element_blank(),
        panel.grid = element_blank())

Mn_labels <- data.frame(
  x = c(0,0.23099,0.46199,0.69298,0.92397,1.15497,1.38596,1.61696,1.84795,2.07894,0.23099,0.46199,0.69298,0.92397,1.15497,1.38596,1.61696,1.84795,2.07894),
  label = c("0","0.23","0.46","0.69","0.92","1.15","1.39","1.62","1.85","2.08","\n0.2","\n0.4","\n0.6","\n0.8","\n1.0","\n1.2","\n1.4","\n1.6","\n1.8"))
S4B4 <- vgraph_Mn %>%
  ggplot(aes(x=mM, y=Mean, shape=as.character(trial), color=conc)) +
  geom_rect(aes(ymin =0, ymax=0.029, xmin=0, xmax=2.31), fill="grey90", color="transparent", alpha=0.25) + 
  geom_rect(aes(ymin = 0.312, ymax=0.34, xmin=0, xmax=2.31), fill="grey90", color="transparent", alpha=0.25) + 
  geom_vline(xintercept = 0.23099, linetype=3) + #mM of EC50 times 0.2
  geom_vline(xintercept = 0.46199, linetype=3) + #mM of EC50 times 0.4
  geom_vline(xintercept = 0.69298, linetype=3) + #mM of EC50 times 0.6
  geom_vline(xintercept = 0.92397, linetype=3) + #mM of EC50 times 0.8
  geom_vline(xintercept = 1.15497, size=2, color="#FD73FF") + #mM of EC50 times 1
  geom_vline(xintercept = 1.38596, linetype=3) + #mM of EC50 times 1.2
  geom_vline(xintercept = 1.61696, linetype=3) + #mM of EC50 times 1.4
  geom_vline(xintercept = 1.84795, linetype=3) + #mM of EC50 times 1.6
  geom_vline(xintercept = 2.07894, linetype=3) + #mM of EC50 times 1.8
  geom_function(fun = ~ my_fn(max=0.33055, c=.x, EC50=1.14189, beta=4.37898)) +
  geom_point(size=4.5) +
  labs(x="Metal Concentration (mM)\nStressor Instensity (x*EC50)", y="m") +
  scale_color_manual(values=bw_palette_5conc) +
  scale_x_continuous(limits = c(0,2.31), 
                     expand = c(0, 0),
                     breaks = Mn_labels$x,
                     labels = Mn_labels$label,
                     minor_breaks = NULL) + 
  scale_y_continuous(limits = c(0,0.34), expand = c(0, 0), breaks = (c(0.0,0.05,0.1,0.15,0.2,0.25,0.3))) +
  theme_bw(base_size = 13) +
  theme(legend.position="none",
        axis.title = element_blank(),
        panel.grid = element_blank())

Ni_labels <- data.frame(
  x = c(0,0.56726,1.13451,1.70177,2.26903,2.83628,3.40354,3.97080,4.53805,5.10531,0.56726,1.13451,1.70177,2.26903,2.83628,3.40354,3.97080,4.53805,5.10531),
  label = c("0","0.57","1.13","1.70","2.27","2.84","3.40","3.97","4.54","5.11","\n0.2","\n0.4","\n0.6","\n0.8","\n1.0","\n1.2","\n1.4","\n1.6","\n1.8"))
S4B5 <- vgraph_Ni %>%
  ggplot(aes(x=mM, y=Mean, shape=as.character(trial), color=conc)) +
  geom_rect(aes(ymin =0, ymax=0.029, xmin=0, xmax=5.67), fill="grey90", color="transparent", alpha=0.25) + 
  geom_rect(aes(ymin = 0.312, ymax=0.34, xmin=0, xmax=5.67), fill="grey90", color="transparent", alpha=0.25) + 
  geom_vline(xintercept = 0.56726, linetype=3) + #mM of EC50 times 0.2
  geom_vline(xintercept = 1.13451, linetype=3) + #mM of EC50 times 0.4
  geom_vline(xintercept = 1.70177, linetype=3) + #mM of EC50 times 0.6
  geom_vline(xintercept = 2.26903, linetype=3) + #mM of EC50 times 0.8
  geom_vline(xintercept = 2.83628, size=2, color="#ffd000") + #mM of EC50 times 1
  geom_vline(xintercept = 3.40354, linetype=3) + #mM of EC50 times 1.2
  geom_vline(xintercept = 3.97080, linetype=3) + #mM of EC50 times 1.4
  geom_vline(xintercept = 4.53805, linetype=3) + #mM of EC50 times 1.6
  geom_vline(xintercept = 5.10531, linetype=3) + #mM of EC50 times 1.8
  geom_function(fun = ~ my_fn(max=0.3332, c=.x, EC50=2.831324, beta=11.62968)) +
  geom_point(size=4.5) +
  labs(x="Metal Concentration (mM)\nStressor Instensity (x*EC50)", y="m") +
  scale_color_manual(values=bw_palette_5conc) +
  scale_x_continuous(limits = c(0,5.67), 
                     expand = c(0, 0),
                     breaks = Ni_labels$x,
                     labels = Ni_labels$label,
                     minor_breaks = NULL) + 
  scale_y_continuous(limits = c(0,0.34), expand = c(0, 0), breaks = (c(0.0,0.05,0.1,0.15,0.2,0.25,0.3))) +
  theme_bw(base_size = 13) +
  theme(legend.position="none",
        axis.title = element_blank(),
        axis.text.y = element_blank(),
        panel.grid = element_blank())

Zn_labels <- data.frame(
  x = c(0,0.96909,1.93819,2.90728,3.87637,4.84546,5.81456,6.78365,7.75274,8.72183,0.96909,1.93819,2.90728,3.87637,4.84546,5.81456,6.78365,7.75274,8.72183),
  label = c("0","0.97","1.94","2.91","3.88","4.85","5.81","6.78","7.75","8.72","\n0.2","\n0.4","\n0.6","\n0.8","\n1","\n1.2","\n1.4","\n1.6","\n1.8"))
S4B6 <- vgraph_Zn %>%
  ggplot(aes(x=mM, y=Mean, shape=as.character(trial), color=conc)) +
  geom_rect(aes(ymin =0, ymax=0.029, xmin=0, xmax=9.69), fill="grey90", color="transparent", alpha=0.25) + 
  geom_rect(aes(ymin = 0.312, ymax=0.34, xmin=0, xmax=9.69), fill="grey90", color="transparent", alpha=0.25) + 
  geom_vline(xintercept = 0.96909, linetype=3) + #mM of EC50 times 0.2
  geom_vline(xintercept = 1.93819, linetype=3) + #mM of EC50 times 0.4
  geom_vline(xintercept = 2.90728, linetype=3) + #mM of EC50 times 0.6
  geom_vline(xintercept = 3.87637, linetype=3) + #mM of EC50 times 0.8
  geom_vline(xintercept = 4.84546, size=2, color="#A880FF") + #mM of EC50 times 1
  geom_vline(xintercept = 5.81456, linetype=3) + #mM of EC50 times 1.2
  geom_vline(xintercept = 6.78365, linetype=3) + #mM of EC50 times 1.4
  geom_vline(xintercept = 7.75274, linetype=3) + #mM of EC50 times 1.6
  geom_vline(xintercept = 8.72183, linetype=3) + #mM of EC50 times 1.8
  geom_function(fun = ~ my_fn(max=0.323794, c=.x, EC50=4.866965, beta=4.579189)) +
  geom_point(size=4.5) +
  labs(x="Metal Concentration (mM)\nStressor Instensity (x*EC50)", y="m") +
  scale_color_manual(values=bw_palette_5conc) +
  scale_x_continuous(limits = c(0,9.69), 
                     expand = c(0, 0),
                     breaks = Zn_labels$x,
                     labels = Zn_labels$label,
                     minor_breaks = NULL) + 
  scale_y_continuous(limits = c(0,0.34), expand = c(0, 0), breaks = (c(0.0,0.05,0.1,0.15,0.2,0.25,0.3))) +
  theme_bw(base_size = 13) +
  theme(legend.position="none",
        axis.title = element_blank(),
        axis.text.y = element_blank(),
        panel.grid = element_blank())
```
%##FigS4_cowplot - NEED TO FINISH
%```{r}
%#figS4B <- 
S4B_plots <- plot_grid(S4B1, S4B2, S4B3, S4B4, S4B5, S4B6, nrow = 2, rel_widths = c(1,0.88,0.88,1,0.88,0.88))
S4B_complete <- plot_grid(NULL, S4B_plots, nrow=1, rel_widths = c(0.05, 1)) +
  #draw_te
%```

#Figure S5
```{r}
CuNi_all <- combodata_avg %>% 
  filter(metal=="Cu" | metal=="CuNi" | metal=="Ni") %>% 
  mutate(combo="CuNi")
CuNi_all$conc <- as.integer(CuNi_all$conc)

CoZn_all <- combodata_avg %>% 
  filter(metal=="Co" | metal=="CoZn" | metal=="Zn") %>% 
  mutate(combo="CoZn")
CoZn_all$conc <- as.integer(CoZn_all$conc)

CoCu_all <- combodata_avg %>% 
  filter(metal=="Co" | metal=="CoCu" | metal=="Cu") %>% 
  mutate(combo="CoCu")
CoCu_all$conc <- as.integer(CoCu_all$conc)

CdCo_all <- combodata_avg %>% 
  filter(metal=="Cd" | metal=="CdCo" | metal=="Co") %>% 
  mutate(combo="CdCo")
CdCo_all$conc <- as.integer(CdCo_all$conc)

CoNi_all <- combodata_avg %>% 
  filter(metal=="Co" | metal=="CoNi" | metal=="Ni") %>% 
  mutate(combo="CoNi")
CoNi_all$conc <- as.integer(CoNi_all$conc)

CuZn_all <- combodata_avg %>% 
  filter(metal=="Cu" | metal=="CuZn" | metal=="Zn") %>% 
  mutate(combo="CuZn")
CuZn_all$conc <- as.integer(CuZn_all$conc)

deltas_unavg_all <- rbind(deltas_unavg_4conc, deltas_conc5)
deltas_unavg_all$conc <- as.integer(deltas_unavg_all$conc)

showcase_deltas <- rbind(CuNi_all, CoZn_all, CoCu_all, CdCo_all, CoNi_all, CuZn_all) %>%
  mutate(metal = case_when(metal==str_extract(combo, "^.{2}") ~ "Met1",
                           metal==combo ~ "Combo",
                           metal==str_extract(combo, ".{2}$") ~ "Met2")) %>% 
  left_join(deltas_unavg_all, by=join_by(combo, conc, trial))

showcase_deltas$conc <- as.integer(showcase_deltas$conc)
showcase_deltas$metal <- factor(showcase_deltas$metal, levels=c("Met1", "Combo", "Met2"))
showcase_deltas$trial <- as.character(showcase_deltas$trial)
showcase_deltas$conc <- factor(showcase_deltas$conc, levels=c("5","4","3","2","1"))

showcase_deltas_conc5_trial1 <- showcase_deltas %>% filter(conc==5 & trial=="one") 
showcase_deltas_conc5_trial2 <- showcase_deltas %>% filter(conc==5 & trial=="two")

showcase_deltas %>%   
  filter(conc!=5) %>% 
  ggplot(aes(x=metal, y=Mean_r, group=interaction(combo,conc,trial), colour=delta_r)) +
  geom_hline(yintercept = 0.0238344) +
  geom_line(linewidth=1) + 
  geom_point(size=3, shape=20) + 
  geom_line(data=showcase_deltas_conc5_trial2, linewidth=1.2) + 
  geom_point(data=showcase_deltas_conc5_trial2, size=3, shape=15) + 
  geom_line(data=showcase_deltas_conc5_trial1, linewidth=1.2) + 
  geom_point(data=showcase_deltas_conc5_trial1, size=3, shape=15) + 
  #scale_colour_gradient(low = "#262626", high = "#d9d9d9") +
  scale_x_discrete(labels=c("Met1" = "Metal 1", "Combo" = "Combo", "Met2" = "Metal 2")) +
  labs(x="Environment", y="r", color="\u03b4", shape="trial") +
  theme_light() +
  theme(panel.grid.minor = element_blank(),
        axis.title.y=element_text(face="bold.italic"),
        axis.title.x=element_text(face="bold")) +
  guides(color = guide_colorbar(order = 1),
         shape = guide_legend(order = 0)) +
  facet_wrap(~combo, ncol=3)
ggsave("FigureOutput/FigS5.png", height=5, width=7,units="in", dpi=700)
```
#Figure S6
##lm stats for delta over concentrations
```{r}
#individual lms
test_CdCo <- deltas_unavg_4conc %>% filter(combo=="CdCo")
lm_CdCo <- lm(delta_r~as.numeric(conc), data=test_CdCo)
lm_CdCo %>% summary()

test_CdCu <- deltas_unavg_4conc %>% filter(combo=="CdCu")
lm_CdCu <- lm(delta_r~as.numeric(conc), data=test_CdCu) 
lm_CdCu %>% summary() # p<0.01 ** slope=+0.10338

test_CdMn <- deltas_unavg_4conc %>% filter(combo=="CdMn")
lm_CdMn <- lm(delta_r~as.numeric(conc), data=test_CdMn) 
lm_CdMn %>% summary()

test_CdNi <- deltas_unavg_4conc %>% filter(combo=="CdNi")
lm_CdNi <- lm(delta_r~as.numeric(conc), data=test_CdNi) 
lm_CdNi %>% summary()

test_CdZn <- deltas_unavg_4conc %>% filter(combo=="CdZn")
lm_CdZn <- lm(delta_r~as.numeric(conc), data=test_CdZn) 
lm_CdZn %>% summary() # p<0.05 * slope=+0.09385

test_CoCu <- deltas_unavg_4conc %>% filter(combo=="CoCu")
lm_CoCu <- lm(delta_r~as.numeric(conc), data=test_CoCu) 
lm_CoCu %>% summary()

test_CoMn <- deltas_unavg_4conc %>% filter(combo=="CoMn")
lm_CoMn <- lm(delta_r~as.numeric(conc), data=test_CoMn)
lm_CoMn %>% summary()

test_CoNi <- deltas_unavg_4conc %>% filter(combo=="CoNi")
lm_CoNi <- lm(delta_r~as.numeric(conc), data=test_CoNi)
lm_CoNi%>% summary() # p<0.10 . slope=-0.10039

test_CoZn <- deltas_unavg_4conc %>% filter(combo=="CoZn")
lm_CoZn <- lm(delta_r~as.numeric(conc), data=test_CoZn)
lm_CoZn %>% summary() # p<0.10 . slope=-0.04022

test_CuMn <- deltas_unavg_4conc %>% filter(combo=="CuMn")
lm_CuMn <- lm(delta_r~as.numeric(conc), data=test_CuMn)
lm_CuMn %>% summary()

test_CuNi <- deltas_unavg_4conc %>% filter(combo=="CuNi")
lm_CuNi <- lm(delta_r~as.numeric(conc), data=test_CuNi)
lm_CuNi %>% summary()

test_CuZn <- deltas_unavg_4conc %>% filter(combo=="CuZn")
lm_CuZn <- lm(delta_r~as.numeric(conc), data=test_CuZn)
lm_CuZn %>% summary()# p<0.05 * slope=-0.018764

test_MnNi <- deltas_unavg_4conc %>% filter(combo=="MnNi")
lm_MnNi <- lm(delta_r~as.numeric(conc), data=test_MnNi)
lm_MnNi %>% summary()# p<0.05 * slope=+0.08334
test_MnZn <- deltas_unavg_4conc %>% filter(combo=="MnZn")
lm_MnZn <- lm(delta_r~as.numeric(conc), data=test_MnZn)
lm_MnZn %>% summary()# p<0.05 * slope=-0.04385

test_NiZn <- deltas_unavg_4conc %>% filter(combo=="NiZn")
lm_NiZn <- lm(delta_r~as.numeric(conc), data=test_NiZn)
lm_NiZn %>% summary()

lm_results_table <- deltas_unavg_4conc %>% ungroup() %>% select(combo) %>% distinct()
lm_results_table$pval <- c(summary(lm_CdCo)$coefficients[2,4],
                           summary(lm_CdCu)$coefficients[2,4],
                           summary(lm_CdMn)$coefficients[2,4],
                           summary(lm_CdNi)$coefficients[2,4],
                           summary(lm_CdZn)$coefficients[2,4],
                           summary(lm_CoCu)$coefficients[2,4],
                           summary(lm_CoMn)$coefficients[2,4],
                           summary(lm_CoNi)$coefficients[2,4],
                           summary(lm_CoZn)$coefficients[2,4],
                           summary(lm_CuMn)$coefficients[2,4],
                           summary(lm_CuNi)$coefficients[2,4],
                           summary(lm_CuZn)$coefficients[2,4],
                           summary(lm_MnNi)$coefficients[2,4],
                           summary(lm_MnZn)$coefficients[2,4],
                           summary(lm_NiZn)$coefficients[2,4])
lm_results_table$slope <- c(summary(lm_CdCo)$coefficients[2,1],
                            summary(lm_CdCu)$coefficients[2,1],
                            summary(lm_CdMn)$coefficients[2,1],
                            summary(lm_CdNi)$coefficients[2,1],
                            summary(lm_CdZn)$coefficients[2,1],
                            summary(lm_CoCu)$coefficients[2,1],
                            summary(lm_CoMn)$coefficients[2,1],
                            summary(lm_CoNi)$coefficients[2,1],
                            summary(lm_CoZn)$coefficients[2,1],
                            summary(lm_CuMn)$coefficients[2,1],
                            summary(lm_CuNi)$coefficients[2,1],
                            summary(lm_CuZn)$coefficients[2,1],
                            summary(lm_MnNi)$coefficients[2,1],
                            summary(lm_MnZn)$coefficients[2,1],
                            summary(lm_NiZn)$coefficients[2,1])
```
## figS6 - trends in delta over concentrations
```{r}
#final graph reflecting significant trends
deltas_unavg_trends <- deltas_unavg_4conc %>% 
  mutate(sig=case_when(combo=="CdCu" ~ "a",
                       combo=="CdZn" ~ "a",
                       combo=="CuZn" ~ "a",
                       combo=="MnNi" ~ "a",
                       combo=="MnZn" ~ "a",
                       .default = "b"))

deltas_unavg_trends %>% 
  ggplot(aes(x=as.numeric(conc), y=delta_r, color=combo)) +
  geom_smooth(method = "lm", aes(linetype = sig), fill="grey80") +  
  geom_point() +
  scale_color_manual(values=combo_alphabet_palette) +
  labs(x="Concentration level", y="\u03b4") +
  theme_bw() +
  theme(legend.position = "none",
        panel.grid.minor = element_blank(),
        axis.title = element_text(face="bold")) +
  facet_wrap(~combo, ncol=5, nrow=3)
ggsave("FigureOutput/FigS6.pdf", height=6, width=7, units="in", dpi=700)
```
###variance of delta in each combo
```{r}
d_vars <- c(var(test_CdCo$delta_r),
            var(test_CdCu$delta_r),
            var(test_CdMn$delta_r),
            var(test_CdNi$delta_r),
            var(test_CdZn$delta_r),
            var(test_CoCu$delta_r),
            var(test_CoMn$delta_r),
            var(test_CoNi$delta_r),
            var(test_CoZn$delta_r),
            var(test_CuMn$delta_r),
            var(test_CuNi$delta_r),
            var(test_CuZn$delta_r),
            var(test_MnNi$delta_r),
            var(test_MnZn$delta_r),
            var(test_NiZn$delta_r))

d_vars
mean(d_vars)
sd(d_vars)
```
#Figure S8
relationship a and delta calculated from r or OD
```{r}
aOD <- read.csv("DataInput/ParameterTableOD.csv") %>% select(Combo, a) %>% 
  rename("combo" = Combo) %>% 
  rename("a_OD" = a)
deltaOD <- delta_OD_df %>%
  filter(conc!=5) %>% 
  group_by(combo) %>% 
  summarise(avg_delta_changeOD = mean(delta_changeOD))

a_comparison <- a_values %>%
  rename(a_r = "a") %>% 
  left_join(aOD)

figS8A <- 
  a_comparison %>% 
  ggplot(aes(x=a_r, y=a_OD)) + 
  geom_hline(yintercept = 0, alpha=0.2) +
  geom_vline(xintercept = 0, alpha=0.2) +
  geom_abline(slope=1, linetype=3) +
  geom_point(aes(color=combo), size=4) +
  geom_abline(slope=1.1924, intercept=0.1086) +
  #geom_smooth(method = "lm", se=F, color="black") +
  scale_color_manual(values=combo_alphabet_palette) +
  labs(x="a(r)", y="a(OD)") +
  xlim(-2.81,3.5) +
  ylim(-2.81,3.5) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        aspect.ratio = 1,
        axis.title=element_text(face="bold"),
        legend.position="none")

########

delta_comparison <- deltas_avg %>% 
  select(combo, avg_delta) %>%
  rename(avg_delta_r="avg_delta") %>% 
  distinct() %>% 
  left_join(deltaOD)

figS8B <- delta_comparison %>% 
  ggplot(aes(x=avg_delta_r, y=avg_delta_changeOD)) + 
  geom_hline(yintercept = 0, alpha=0.2) +
  geom_vline(xintercept = 0, alpha=0.2) +
  geom_abline(slope=1, linetype=3) +
  geom_point(aes(color=combo), size=4) +
  geom_abline(slope=1.1618, intercept=-0.0833) +
  #geom_smooth(method = "lm", se=F, color="black") +
  scale_color_manual(values=combo_alphabet_palette) +
  scale_x_continuous(breaks = c(0.0,0.5,1.0), limits = c(-0.22,1)) +
  scale_y_continuous(breaks = c(0.0,0.5,1.0), limits = c(-0.22,1)) +
  labs(x="delta(r)", y="delta(OD)") +
  #xlim(-0.22,0.95) +
  #ylim(-0.22,0.95) +
  theme_bw() +
  theme(panel.grid = element_blank(),
        aspect.ratio = 1,
        axis.title=element_text(face="bold"),
        legend.position="none")

figS8_graphs <- plot_grid(figS8A, figS8B, labels = "AUTO", nrow = 1, rel_widths = c(1,1.007))
plot_grid(figS8_graphs, NULL, fig5_legend, nrow = 1, rel_widths = c(1,0.01,0.1))
ggsave2("FigureOutput/FigS8.pdf", height = 4.9, width = 9.5, units = "in", dpi=1000)


#DEMING REGRESSIONS
(sd(a_comparison$a_OD)^2)/(sd(a_comparison$a_r)^2) #calculating error ratio
dem_reg(x="a_r", y="a_OD", data=a_comparison, error.ratio = 1.27)
(sd(delta_comparison$avg_delta_changeOD)^2)/(sd(delta_comparison$avg_delta_r)^2) #calculating error ratio
dem_reg(x="avg_delta_r", y="avg_delta_changeOD", data=delta_comparison, error.ratio = 1.31)
```

#Figure S9
literature review
```{r}
literature <- read.csv("DataInput/metal_mixture_literature_data.csv") %>% 
  left_join(a_values) %>% 
  rename(a_value = "a") %>% 
  mutate(interaction.value=case_when(interaction=="antagonism" ~ 1,
                                     interaction=="additivity/antagonism" ~ 0.5,
                                     interaction=="additivity" ~ 0,
                                     interaction=="additivity/synergism" ~ -0.5,
                                     interaction=="synergism" ~ -1,
                                     .default=NA)) %>% 
  filter(First.author!="Kahn") %>% 
  filter(Year>1999) 
  
lit_counts <- literature %>% 
  group_by(combo) %>% 
  summarise(ncombo=n())

threecombos <- literature %>% 
  filter(combo=="CdCu" | combo=="CdZn" | combo=="CuZn") 
three_combos_avg <- threecombos %>% 
  group_by(combo) %>% 
  summarise(avg_synant=mean(interaction.value)) %>% 
  left_join(a_values) %>% 
  left_join(lit_counts) %>% 
  rename(a_value = "a")

lm(avg_synant ~ a_value, data=three_combos_avg) %>% summary()

three_combos_avg %>% 
  ggplot(aes(x=a_value, y=avg_synant, color=combo)) +
  geom_smooth(method="lm", se=F, data=three_combos_avg, inherit.aes = F, aes(x=a_value, y=avg_synant), color="black") +
  geom_point(size=6) +
  geom_jitter(data=threecombos, aes(x=a_value, y=interaction.value), height=0.02, width=0.02, size=1, color="black") +
  scale_color_manual(values=c("#90B927","#D48D8B","#3C99DB")) +
  labs(x="a",y="Interaction type", color="Metal\ncombination") +
  theme_bw(base_size=14) +
  theme(panel.grid = element_blank(),
        axis.title.x = element_text(face="bold.italic", family="serif", size=16),
        axis.title.y = element_text(face="bold"))
ggsave("FigureOutput/FigS9.pdf", height=5, width=6, units = "in")
```
